---
title: "MM_SupplementalAnalyses"
author: "Jennifer Mosley"
date: "2024-09-08"
output:
  html_document: default
  word_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyr)
library(broom.mixed)
library(dplyr)
library(lubridate)
library(lmerTest)
library(gtsummary)
library(report)
library(kableExtra)
library(sjPlot)
library(ggplot2)
library(partR2)
library(effects)
```

## Supplemental Analyses - Individual Differences/Self-Report Analysis

```{r}
# Import datasets and merge

# Import individual differences (ID) data set
Df <- read.csv("cleaned_S1.csv")
Df <- Df[-c(1)]
Df <- Df[-c(684)] # Remove check column

subID <- select(Df,c("loginID"))
ID <- Df[ ,639:729]

data <- cbind(subID,ID) # Use this for individual differences/demo analysis

# Import centrality data set
cent <- read.csv("centralityDf_48.csv")
cent <- cent[-c(1)] # Remove extraneous column in front
# Remove sub22 from the centrality dataset, as they are not included in the in-scan ratings data
cent <- cent[cent$subID != "22", ]

# Import density data set
dense <- read.csv("density.csv")
dense <- dense[-c(1)] # Remove extraneous column in front

netmetrics <- cbind(cent,dense)

# Import in-scan memory ratings
inscan <- read.csv("scan_ratings.csv")
inscan <- inscan[-c(1)] # Remove extraneous column in front

fullData <- read.csv("fullData48.csv")
fullData <- fullData[-c(1)] # Remove extraneous column in front
fullData <- fullData[fullData$subID != 22, ]

```

# Individual Differences

## Recode/Reverse scores
```{r}
# Rosenberg Self-Esteem Scale
RSE <- data[2:11]

RSE <- RSE %>%
  mutate(RSE3 = case_when(
    RSE3 == 1 ~ 4,
    RSE3 == 2 ~ 3,
    RSE3 == 4 ~ 1,
    RSE3 == 3 ~ 2,
    TRUE ~ RSE3  # Keep the original value if none of the conditions are met
  ))

RSE <- RSE %>%
  mutate(RSE5 = case_when(
    RSE5 == 1 ~ 4,
    RSE5 == 2 ~ 3,
    RSE5 == 4 ~ 1,
    RSE5 == 3 ~ 2,
    TRUE ~ RSE5  # Keep the original value if none of the conditions are met
  ))

RSE <- RSE %>%
  mutate(RSE8 = case_when(
    RSE8 == 1 ~ 4,
    RSE8 == 2 ~ 3,
    RSE8 == 4 ~ 1,
    RSE8 == 3 ~ 2,
    TRUE ~ RSE8  # Keep the original value if none of the conditions are met
  ))

RSE <- RSE %>%
  mutate(RSE9 = case_when(
    RSE9 == 1 ~ 4,
    RSE9 == 2 ~ 3,
    RSE9 == 4 ~ 1,
    RSE9 == 3 ~ 2,
    TRUE ~ RSE9  # Keep the original value if none of the conditions are met
  ))

RSE <- RSE %>%
  mutate(RSE10 = case_when(
    RSE10 == 1 ~ 4,
    RSE10 == 2 ~ 3,
    RSE10 == 4 ~ 1,
    RSE10 == 3 ~ 2,
    TRUE ~ RSE10  # Keep the original value if none of the conditions are met
  ))

RSE_sum <- rowSums(RSE,na.rm = TRUE)
RSE_sum <- as.vector(RSE_sum)

RSE$RSE_sum <- RSE_sum

sums <- select(data,c("loginID"))
sums$RSE <- RSE_sum # Max possible: 40; higher score, higher self-esteem

# Need for Cognition
NFC <- data[12:17]

# Items 3,4 are reverse scored (reverse agreement for low need for cognition)
NFC <- NFC %>%
  mutate(NFC.6_3 = case_when(
    NFC.6_3 == 1 ~ 4,
    NFC.6_3 == 2 ~ 3,
    NFC.6_3 == 4 ~ 1,
    NFC.6_3 == 3 ~ 2,
    TRUE ~ NFC.6_3  # Keep the original value if none of the conditions are met
  ))

NFC <- NFC %>%
  mutate(NFC.6_4 = case_when(
    NFC.6_4 == 1 ~ 4,
    NFC.6_4 == 2 ~ 3,
    NFC.6_4 == 4 ~ 1,
    NFC.6_4 == 3 ~ 2,
    TRUE ~ NFC.6_4  # Keep the original value if none of the conditions are met
  ))

NFC_sum <- rowSums(NFC,na.rm = TRUE)
NFC_sum <- as.vector(NFC_sum)
sums$NFC <-NFC_sum  # Max possible: 30; higher score, higher need for cognition

# Self-Concept Clarity
SCC <- data[18:29]

# Items 1,2,3,4,5,7,8,9,10,12 are reverse scored (reverse agreement for low self-concept clarity)
SCC <- SCC %>%
  mutate(SCC1 = case_when(
    SCC1 == 1 ~ 5,
    SCC1 == 2 ~ 4,
    SCC1 == 4 ~ 2,
    SCC1 == 5 ~ 1,
    TRUE ~ SCC1  # Keep the original value if none of the conditions are met
  ))

SCC <- SCC %>%
  mutate(SCC2 = case_when(
    SCC2 == 1 ~ 5,
    SCC2 == 2 ~ 4,
    SCC2 == 4 ~ 2,
    SCC2 == 5 ~ 1,
    TRUE ~ SCC2  # Keep the original value if none of the conditions are met
  ))

SCC <- SCC %>%
  mutate(SCC3 = case_when(
    SCC3 == 1 ~ 5,
    SCC3 == 2 ~ 4,
    SCC3 == 4 ~ 2,
    SCC3 == 5 ~ 1,
    TRUE ~ SCC3  # Keep the original value if none of the conditions are met
  ))

SCC <- SCC %>%
  mutate(SCC4 = case_when(
    SCC4 == 1 ~ 5,
    SCC4 == 2 ~ 4,
    SCC4 == 4 ~ 2,
    SCC4 == 5 ~ 1,
    TRUE ~ SCC4  # Keep the original value if none of the conditions are met
  ))

SCC <- SCC %>%
  mutate(SCC5 = case_when(
    SCC5 == 1 ~ 5,
    SCC5 == 2 ~ 4,
    SCC5 == 4 ~ 2,
    SCC5 == 5 ~ 1,
    TRUE ~ SCC5  # Keep the original value if none of the conditions are met
  ))

SCC <- SCC %>%
  mutate(SCC7 = case_when(
    SCC7 == 1 ~ 5,
    SCC7 == 2 ~ 4,
    SCC7 == 4 ~ 2,
    SCC7 == 5 ~ 1,
    TRUE ~ SCC7  # Keep the original value if none of the conditions are met
  ))

SCC <- SCC %>%
  mutate(SCC8 = case_when(
    SCC8 == 1 ~ 5,
    SCC8 == 2 ~ 4,
    SCC8 == 4 ~ 2,
    SCC8 == 5 ~ 1,
    TRUE ~ SCC8  # Keep the original value if none of the conditions are met
  ))

SCC <- SCC %>%
  mutate(SCC9 = case_when(
    SCC9 == 1 ~ 5,
    SCC9 == 2 ~ 4,
    SCC9 == 4 ~ 2,
    SCC9 == 5 ~ 1,
    TRUE ~ SCC9  # Keep the original value if none of the conditions are met
  ))

SCC <- SCC %>%
  mutate(SCC10 = case_when(
    SCC10 == 1 ~ 5,
    SCC10 == 2 ~ 4,
    SCC10 == 4 ~ 2,
    SCC10 == 5 ~ 1,
    TRUE ~ SCC10  # Keep the original value if none of the conditions are met
  ))

SCC <- SCC %>%
  mutate(SCC12 = case_when(
    SCC12 == 1 ~ 5,
    SCC12 == 2 ~ 4,
    SCC12 == 4 ~ 2,
    SCC12 == 5 ~ 1,
    TRUE ~ SCC12  # Keep the original value if none of the conditions are met
  ))

SCC_sum <- rowSums(SCC,na.rm = TRUE)
SCC_sum <- as.vector(SCC_sum)
sums$SCC <- SCC_sum # Max possible: 60; higher score, higher self-concept clarity


# S-DS, Self-Discrepancy Scale
DSS <- data[30:43]

# Items 1,5,6,7,9,14 are reverse scored
DSS <- DSS %>%
  mutate(DS.S_1 = case_when(
    DS.S_1 == 1 ~ 7,
    DS.S_1 == 2 ~ 6,
    DS.S_1 == 7 ~ 1,
    DS.S_1 == 6 ~ 2,
    TRUE ~ DS.S_1  # Keep the original value if none of the conditions are met
  ))

DSS <- DSS %>%
  mutate(DS.S_5 = case_when(
    DS.S_5 == 1 ~ 7,
    DS.S_5 == 2 ~ 6,
    DS.S_5 == 7 ~ 1,
    DS.S_5 == 6 ~ 2,
    TRUE ~ DS.S_5  # Keep the original value if none of the conditions are met
  ))

DSS <- DSS %>%
  mutate(DS.S_6 = case_when(
    DS.S_6 == 1 ~ 7,
    DS.S_6 == 2 ~ 6,
    DS.S_6 == 7 ~ 1,
    DS.S_6 == 6 ~ 2,
    TRUE ~ DS.S_6  # Keep the original value if none of the conditions are met
  ))

DSS <- DSS %>%
  mutate(DS.S_7 = case_when(
    DS.S_7 == 1 ~ 7,
    DS.S_7 == 2 ~ 6,
    DS.S_7 == 7 ~ 1,
    DS.S_7 == 6 ~ 2,
    TRUE ~ DS.S_7  # Keep the original value if none of the conditions are met
  ))

DSS <- DSS %>%
  mutate(DS.S_9 = case_when(
    DS.S_9 == 1 ~ 7,
    DS.S_9 == 2 ~ 6,
    DS.S_9 == 7 ~ 1,
    DS.S_9 == 6 ~ 2,
    TRUE ~ DS.S_9  # Keep the original value if none of the conditions are met
  ))

DSS <- DSS %>%
  mutate(DS.S_14 = case_when(
    DS.S_14 == 1 ~ 7,
    DS.S_14 == 2 ~ 6,
    DS.S_14 == 7 ~ 1,
    DS.S_14 == 6 ~ 2,
    TRUE ~ DS.S_14  # Keep the original value if none of the conditions are met
  ))

DSS_sum <- rowSums(DSS,na.rm = TRUE)
DSS_sum <- as.vector(DSS_sum)
sums$DSS <- DSS_sum # Max possible: 98; Higher score, higher self-discrepancy (lower self-concept clarity)

# Center for Epidemiologic Studies Depression Scale (CESD)
CESD <- data[44:63]

# Items 4,8,12,16 are reverse scored
CESD <- CESD %>%
  mutate(CESD4 = case_when(
    CESD4 == 1 ~ 4,
    CESD4 == 2 ~ 3,
    CESD4 == 4 ~ 1,
    CESD4 == 3 ~ 2,
    TRUE ~ CESD4  # Keep the original value if none of the conditions are met
  ))

CESD <- CESD %>%
  mutate(CESD8 = case_when(
    CESD8 == 1 ~ 4,
    CESD8 == 2 ~ 3,
    CESD8 == 4 ~ 1,
    CESD8 == 3 ~ 2,
    TRUE ~ CESD8  # Keep the original value if none of the conditions are met
  ))

CESD <- CESD %>%
  mutate(CESD12 = case_when(
    CESD12 == 1 ~ 4,
    CESD12 == 2 ~ 3,
    CESD12 == 4 ~ 1,
    CESD12 == 3 ~ 2,
    TRUE ~ CESD12  # Keep the original value if none of the conditions are met
  ))

CESD <- CESD %>%
  mutate(CESD16 = case_when(
    CESD16 == 1 ~ 4,
    CESD16 == 2 ~ 3,
    CESD16 == 4 ~ 1,
    CESD16 == 3 ~ 2,
    TRUE ~ CESD16  # Keep the original value if none of the conditions are met
  ))

CESD_sum <- rowSums(CESD,na.rm = TRUE)
CESD_sum <- as.vector(CESD_sum)
sums$CESD <- CESD_sum # Max possible: 60; Higher score, higher depressive symptomatology

# Subjective Happiness Scale (SHS)
SHS <- data[64:67]

# Items 4 is reversed scored
SHS <- SHS %>%
  mutate(SHS4 = case_when(
    SHS4 == 7 ~ 1,
    SHS4 == 6 ~ 2,
    SHS4 == 1 ~ 7,
    SHS4 == 2 ~ 6,
    TRUE ~ SHS4  # Keep the original value if none of the conditions are met
  ))

SHS_sum <- rowSums(SHS,na.rm = TRUE)
SHS_sum <- as.vector(SHS_sum)
sums$SHS <- SHS_sum # Max possible: 28; Higher score, higher subjective happiness

# Rumination-Reflection Questionnaire (RRQ)
RRQ <- data[68:91]

# Items 6,9,10,13,14,17,20,24 is reversed scored
RRQ <- RRQ %>%
  mutate(RRQ_6 = case_when(
    RRQ_6 == 5 ~ 1,
    RRQ_6 == 2 ~ 2,
    RRQ_6 == 1 ~ 5,
    RRQ_6 == 2 ~ 4,
    TRUE ~ RRQ_6  # Keep the original value if none of the conditions are met
  ))

RRQ <- RRQ %>%
  mutate(RRQ_9 = case_when(
    RRQ_9 == 5 ~ 1,
    RRQ_9 == 2 ~ 2,
    RRQ_9 == 1 ~ 5,
    RRQ_9 == 2 ~ 4,
    TRUE ~ RRQ_9  # Keep the original value if none of the conditions are met
  ))

RRQ <- RRQ %>%
  mutate(RRQ_10 = case_when(
    RRQ_10 == 5 ~ 1,
    RRQ_10 == 2 ~ 2,
    RRQ_10 == 1 ~ 5,
    RRQ_10 == 2 ~ 4,
    TRUE ~ RRQ_10  # Keep the original value if none of the conditions are met
  ))

RRQ <- RRQ %>%
  mutate(RRQ_13 = case_when(
    RRQ_13 == 5 ~ 1,
    RRQ_13 == 2 ~ 2,
    RRQ_13 == 1 ~ 5,
    RRQ_13 == 2 ~ 4,
    TRUE ~ RRQ_13  # Keep the original value if none of the conditions are met
  ))

RRQ <- RRQ %>%
  mutate(RRQ_14 = case_when(
    RRQ_14 == 5 ~ 1,
    RRQ_14 == 2 ~ 2,
    RRQ_14 == 1 ~ 5,
    RRQ_14 == 2 ~ 4,
    TRUE ~ RRQ_14  # Keep the original value if none of the conditions are met
  ))

RRQ <- RRQ %>%
  mutate(RRQ_17 = case_when(
    RRQ_17 == 5 ~ 1,
    RRQ_17 == 2 ~ 2,
    RRQ_17 == 1 ~ 5,
    RRQ_17 == 2 ~ 4,
    TRUE ~ RRQ_17  # Keep the original value if none of the conditions are met
  ))

RRQ <- RRQ %>%
  mutate(RRQ_20 = case_when(
    RRQ_20 == 5 ~ 1,
    RRQ_20 == 2 ~ 2,
    RRQ_20 == 1 ~ 5,
    RRQ_20 == 2 ~ 4,
    TRUE ~ RRQ_20  # Keep the original value if none of the conditions are met
  ))

RRQ <- RRQ %>%
  mutate(RRQ_24 = case_when(
    RRQ_24 == 5 ~ 1,
    RRQ_24 == 2 ~ 2,
    RRQ_24 == 1 ~ 5,
    RRQ_24 == 2 ~ 4,
    TRUE ~ RRQ_24  # Keep the original value if none of the conditions are met
  ))


RRQ_Rum <- select(RRQ,c("RRQ_1","RRQ_2","RRQ_3","RRQ_4","RRQ_5","RRQ_6","RRQ_7",
                        "RRQ_8","RRQ_9","RRQ_10","RRQ_11","RRQ_12"))
RRQ_Rum$Rum_mean <- rowMeans(RRQ_Rum, na.rm = TRUE)

RRQ_Ref <- select(RRQ,c("RRQ_13","RRQ_14","RRQ_15","RRQ_16","RRQ_17","RRQ_18","RRQ_19",
                        "RRQ_20","RRQ_21","RRQ_22","RRQ_23","RRQ_24"))
RRQ_Ref$Ref_mean <- rowMeans(RRQ_Ref, na.rm = TRUE)

RRQ <- RRQ %>%
  mutate(Ref_mean = RRQ_Ref$Ref_mean)

RRQ <- RRQ %>%
  mutate(Rum_mean = RRQ_Rum$Rum_mean)

RRQ_stats <- select(RRQ,c("Ref_mean", "Rum_mean"))

sums <- bind_cols(sums, RRQ_stats) # Rumination vs. Reflection
```

## Repeat individual differences for centrality/ratings dataframe
```{r}
repeat_data_df <- function(df, n_times) {
  # Use the `rep()` function to repeat the indices of the dataframe
  repeated_df <- df[rep(1:nrow(df), each = n_times), ]
  
  # Return the repeated dataframe
  return(repeated_df)
}

individual_data <- repeat_data_df(sums, 24)
individual_data <- individual_data[individual_data$loginID != "22", ]
individual_data[individual_data==0] <- NA
```

## Combine all datasets and finalize
```{r}
# Be sure to run the rest of the script before this, depends on dimensions after processing.


# Force combine datasets that are off by a single observation
full_index <- seq_len(max(nrow(individual_data), nrow(netmetrics)))

# Align df1
df1_aligned <- individual_data[full_index, , drop = FALSE]
df1_aligned[is.na(df1_aligned)] <- NA

# Align df2
df2_aligned <- netmetrics[full_index, , drop = FALSE]
df2_aligned[is.na(df2_aligned)] <- NA

# Combine aligned dataframes
data2 <- cbind(df1_aligned, df2_aligned)

data <- cbind(data2,inscan)

# Remove extra subID columns 
data <- select(data, -subID)

# Set numeric columns to numeric
data$valRate <- as.numeric(data$valRate)
data$intenseRate <- as.numeric(data$intenseRate)
data$vividRate <- as.numeric(data$vividRate)

# Remove 22 from sums
sums <- sums[data$loginID != 22, ]

ratings <- fullData[, c(24:29,33)] # Remove extraneous column in front

# Repeat first row of data to pad for later cbind
first_row <- ratings[1, ]
ratings <- rbind(first_row, ratings)
ratings[1, ] <- NA

all <- cbind(data,ratings)

# centUnique <- cent[! duplicated(cent$subID), ]
# sums_cent <- cbind(sums,centUnique) 
# sums_cent <- sums_cent[,-c(10)] # Remove extra subject ID col
# 
# denseUnique <- dense[! duplicated(dense$subID), ]
# sums_dense <- cbind(sums,denseUnique)
# sums_dense <- sums_dense[,-c(10)] # Remove extra subject ID col
```


```{r}
# Set numID
numID = 24
```

# Analyses (lmer)

# Predicting memory RATINGS from outdegree x individual differences
```{r}

m1 <- lmer(scale(transformativeness) ~ scale(RSE) + scale(outdegree) + (scale(RSE) * scale(outdegree)) + (scale(outdegree) | loginID), data=all)
#tab_model(m1)
#summary(m1)
#transRSE_r2 <- partR2(m1)

# RSE_plot <- ggplot(all, aes(x = RSE, y = transformativeness, color = outdegree)) +
#   geom_smooth(method = "lm", se = TRUE) +
#   labs(title = "Self-Esteem Interaction with Transformativeness and Outdegree",
#        x = "Self-Esteem",
#        y = "Self-Transformativeness") +
#   theme_minimal() +
#   theme(
#     axis.title.x = element_text(face = "bold"),   # Make x-axis label bold
#     axis.title.y = element_text(face = "bold"),   # Make y-axis label bold
#     panel.grid.major = element_blank()            # Remove major gridlines
#   )
# 
# plot(RSE_plot)


m12 <- lmer(scale(transformativeness) ~ scale(NFC) + scale(outdegree) + (scale(NFC) * scale(outdegree)) + (scale(outdegree) | loginID), data=all)
m13 <- lmer(scale(transformativeness) ~ scale(SCC) + scale(outdegree) + (scale(SCC) * scale(outdegree)) + (scale(outdegree) | loginID), data=all)
m14 <- lmer(scale(transformativeness) ~ scale(DSS) + scale(outdegree) + (scale(DSS) * scale(outdegree)) + (scale(outdegree) | loginID), data=all)
m15 <- lmer(scale(transformativeness) ~ scale(CESD) + scale(outdegree) + (scale(CESD) * scale(outdegree)) + (scale(outdegree) | loginID), data=all)
m16 <- lmer(scale(transformativeness) ~ scale(SHS) + scale(outdegree) + (scale(SHS) * scale(outdegree)) + (scale(outdegree) | loginID), data=all)
m17 <- lmer(scale(transformativeness) ~ scale(Ref_mean) + scale(outdegree) + (scale(Ref_mean) * scale(outdegree)) + (scale(outdegree) | loginID), data=all)
m18 <- lmer(scale(transformativeness) ~ scale(Rum_mean) + scale(outdegree) + (scale(Rum_mean) * scale(outdegree)) + (scale(outdegree) | loginID), data=all)

tab_model(m1, m12, m13, m14, 
          show.p = TRUE,  # Show p-values
          #show.ci = TRUE, # Show confidence intervals
          show.se = TRUE, # Show standard errors
          title = "Combined Mixed-Effects Model Results")

tab_model(m15, m16, m17, m18, 
          show.p = TRUE,  # Show p-values
          #show.ci = TRUE, # Show confidence intervals
          show.se = TRUE, # Show standard errors
          title = "Combined Mixed-Effects Model Results")

#tbl_regression(m1) %>% as_gt()
#summary(m1)
```

```{r}
m2 <- lmer(scale(valRate) ~ scale(RSE) + scale(outdegree) + (scale(RSE) * scale(outdegree)) + (scale(outdegree) | loginID), data=all)
m21 <- lmer(scale(valRate) ~ scale(NFC) + scale(outdegree) + (scale(NFC) * scale(outdegree)) + (scale(outdegree) | loginID), data=all)
m22 <- lmer(scale(valRate) ~ scale(SCC) + scale(outdegree) + (scale(SCC) * scale(outdegree)) + (scale(outdegree) | loginID), data=all)
m23 <- lmer(scale(valRate) ~ scale(DSS) + scale(outdegree) + (scale(DSS) * scale(outdegree)) + (scale(outdegree) | loginID), data=all)
m24 <- lmer(scale(valRate) ~ scale(CESD) + scale(outdegree) + (scale(CESD) * scale(outdegree)) + (scale(outdegree) | loginID), data=all)
m25 <- lmer(scale(valRate) ~ scale(SHS) + scale(outdegree) + (scale(SHS) * scale(outdegree)) + (scale(outdegree) | loginID), data=all)
m26 <- lmer(scale(valRate) ~ scale(Ref_mean) + scale(outdegree) + (scale(Ref_mean) * scale(outdegree)) + (scale(outdegree) | loginID), data=all)
m27 <- lmer(scale(valRate) ~ scale(Rum_mean) + scale(outdegree) + (scale(Rum_mean) * scale(outdegree)) + (scale(outdegree) | loginID), data=all)

tab_model(m2, m21, m22, m23, 
          show.p = TRUE,  # Show p-values
          #show.ci = TRUE, # Show confidence intervals
          show.se = TRUE, # Show standard errors
          title = "Combined Mixed-Effects Model Results")

tab_model(m24, m25, m26, m27, 
          show.p = TRUE,  # Show p-values
          #show.ci = TRUE, # Show confidence intervals
          show.se = TRUE, # Show standard errors
          title = "Combined Mixed-Effects Model Results")

#tab_model(m2)
#tbl_regression(m1) %>% as_gt()
#summary(m1)
```

```{r}

m3 <- lmer(scale(importance) ~ scale(RSE) + scale(outdegree) + (scale(RSE) * scale(outdegree)) + (scale(outdegree) | loginID), data=all)
tab_model(m3)
summary(m3)
impRSE_r2 <- partR2(m3)
m32 <- lmer(scale(importance) ~ scale(NFC) + scale(outdegree) + (scale(NFC) * scale(outdegree)) + (scale(outdegree) | loginID), data=all)
m33 <- lmer(scale(importance) ~ scale(SCC) + scale(outdegree) + (scale(SCC) * scale(outdegree)) + (scale(outdegree) | loginID), data=all)
#tab_model(m33)
#summary(m33)
#importSCC_r2 <- partR2(m33)
m34 <- lmer(scale(importance) ~ scale(DSS) + scale(outdegree) + (scale(DSS) * scale(outdegree)) + (scale(outdegree) | loginID), data=all)
m35 <- lmer(scale(importance) ~ scale(CESD) + scale(outdegree) + (scale(CESD) * scale(outdegree)) + (scale(outdegree) | loginID), data=all)
m36 <- lmer(scale(importance) ~ scale(SHS) + scale(outdegree) + (scale(SHS) * scale(outdegree)) + (scale(outdegree) | loginID), data=all)
m37 <- lmer(scale(importance) ~ scale(Ref_mean) + scale(outdegree) + (scale(Ref_mean) * scale(outdegree)) + (scale(outdegree) | loginID), data=all)
m38 <- lmer(scale(importance) ~ scale(Rum_mean) + scale(outdegree) + (scale(Rum_mean) * scale(outdegree)) + (scale(outdegree) | loginID), data=all)

tab_model(m3, m32, m33, m34, 
          show.p = TRUE,  # Show p-values
          #show.ci = TRUE, # Show confidence intervals
          show.se = TRUE, # Show standard errors
          title = "Combined Mixed-Effects Model Results")

tab_model(m35, m36, m37, m38, 
          show.p = TRUE,  # Show p-values
          #show.ci = TRUE, # Show confidence intervals
          show.se = TRUE, # Show standard errors
          title = "Combined Mixed-Effects Model Results")

#tab_model(m3)
#tbl_regression(m1) %>% as_gt()
#summary(m1)
```

```{r}

m4 <- lmer(scale(clear) ~ scale(RSE) + scale(outdegree) + (scale(RSE) * scale(outdegree)) + (scale(outdegree) | loginID), data=all)
m42 <- lmer(scale(clear) ~ scale(NFC) + scale(outdegree) + (scale(NFC) * scale(outdegree)) + (scale(outdegree) | loginID), data=all)
m43 <- lmer(scale(clear) ~ scale(SCC) + scale(outdegree) + (scale(SCC) * scale(outdegree)) + (scale(outdegree) | loginID), data=all)
m44 <- lmer(scale(clear) ~ scale(DSS) + scale(outdegree) + (scale(DSS) * scale(outdegree)) + (scale(outdegree) | loginID), data=all)
m45 <- lmer(scale(clear) ~ scale(CESD) + scale(outdegree) + (scale(CESD) * scale(outdegree)) + (scale(outdegree) | loginID), data=all)
m46 <- lmer(scale(clear) ~ scale(SHS) + scale(outdegree) + (scale(SHS) * scale(outdegree)) + (scale(outdegree) | loginID), data=all)
m47 <- lmer(scale(clear) ~ scale(Ref_mean) + scale(outdegree) + (scale(Ref_mean) * scale(outdegree)) + (scale(outdegree) | loginID), data=all)
tab_model(m47)
summary(m47)
clearRef_r2 <- partR2(m47)
m48 <- lmer(scale(clear) ~ scale(Rum_mean) + scale(outdegree) + (scale(Rum_mean) * scale(outdegree)) + (scale(outdegree) | loginID), data=all)


tab_model(m4, m42, m43, m44, 
          show.p = TRUE,  # Show p-values
          #show.ci = TRUE, # Show confidence intervals
          show.se = TRUE, # Show standard errors
          title = "Combined Mixed-Effects Model Results")

tab_model(m45, m46, m47, m48, 
          show.p = TRUE,  # Show p-values
          #show.ci = TRUE, # Show confidence intervals
          show.se = TRUE, # Show standard errors
          title = "Combined Mixed-Effects Model Results")


#tab_model(m4)
#tbl_regression(m1) %>% as_gt()
#summary(m1)
```

```{r}
m5 <- lmer(scale(easy) ~ scale(RSE) + scale(outdegree) + (scale(RSE) * scale(outdegree)) + (scale(outdegree) | loginID), data=all)
m52 <- lmer(scale(easy) ~ scale(NFC) + scale(outdegree) + (scale(NFC) * scale(outdegree)) + (scale(outdegree) | loginID), data=all)
m53 <- lmer(scale(easy) ~ scale(SCC) + scale(outdegree) + (scale(SCC) * scale(outdegree)) + (scale(outdegree) | loginID), data=all)
tab_model(m53) #outdegree is a significant predictor of ease of recall when controlling for self-concept clarity
m54 <- lmer(scale(easy) ~ scale(DSS) + scale(outdegree) + (scale(DSS) * scale(outdegree)) + (scale(outdegree) | loginID), data=all)
m55 <- lmer(scale(easy) ~ scale(CESD) + scale(outdegree) + (scale(CESD) * scale(outdegree)) + (scale(outdegree) | loginID), data=all)
m56 <- lmer(scale(easy) ~ scale(SHS) + scale(outdegree) + (scale(SHS) * scale(outdegree)) + (scale(outdegree) | loginID), data=all)
m57 <- lmer(scale(easy) ~ scale(Ref_mean) + scale(outdegree) + (scale(Ref_mean) * scale(outdegree)) + (scale(outdegree) | loginID), data=all)
m58 <- lmer(scale(easy) ~ scale(Rum_mean) + scale(outdegree) + (scale(Rum_mean) * scale(outdegree)) + (scale(outdegree) | loginID), data=all)

tab_model(m5, m52, m53, m54, 
          show.p = TRUE,  # Show p-values
          #show.ci = TRUE, # Show confidence intervals
          show.se = TRUE, # Show standard errors
          title = "Combined Mixed-Effects Model Results")

tab_model(m55, m56, m57, m58, 
          show.p = TRUE,  # Show p-values
          #show.ci = TRUE, # Show confidence intervals
          show.se = TRUE, # Show standard errors
          title = "Combined Mixed-Effects Model Results")

#tab_model(m5)
#tbl_regression(m1) %>% as_gt()
#summary(m1)
```

```{r}
m6 <- lmer(scale(agency) ~ scale(RSE) + scale(outdegree) + (scale(RSE) * scale(outdegree)) + (scale(outdegree) | loginID), data=all)
m62 <- lmer(scale(agency) ~ scale(NFC) + scale(outdegree) + (scale(NFC) * scale(outdegree)) + (scale(outdegree) | loginID), data=all)
m63 <- lmer(scale(agency) ~ scale(SCC) + scale(outdegree) + (scale(SCC) * scale(outdegree)) + (scale(outdegree) | loginID), data=all)
m64 <- lmer(scale(agency) ~ scale(DSS) + scale(outdegree) + (scale(DSS) * scale(outdegree)) + (scale(outdegree) | loginID), data=all)
m65 <- lmer(scale(agency) ~ scale(CESD) + scale(outdegree) + (scale(CESD) * scale(outdegree)) + (scale(outdegree) | loginID), data=all)
#tab_model(m65)
#summary(m65)
#agencyCESD_r2 <- partR2(m65)
#m65_plot <- ggplot(m65)

#interaction_m65 <- anova(m65)

m66 <- lmer(scale(agency) ~ scale(SHS) + scale(outdegree) + (scale(SHS) * scale(outdegree)) + (scale(outdegree) | loginID), data=all)
tab_model(m66) #outdegree is a significant predictor of agency when controlling for subjective happiness
#summary(m66)
#agencySHS_r2 <- partR2(m66)

#interaction_m66 <- anova(m66)

m67 <- lmer(scale(agency) ~ scale(Ref_mean) + scale(outdegree) + (scale(Ref_mean) * scale(outdegree)) + (scale(outdegree) | loginID), data=all)
m68 <- lmer(scale(agency) ~ scale(Rum_mean) + scale(outdegree) + (scale(Rum_mean) * scale(outdegree)) + (scale(outdegree) | loginID), data=all)

tab_model(m6, m62, m63, m64, 
          show.p = TRUE,  # Show p-values
          #show.ci = TRUE, # Show confidence intervals
          show.se = TRUE, # Show standard errors
          title = "Combined Mixed-Effects Model Results")

tab_model(m65, m66, m67, m68, 
          show.p = TRUE,  # Show p-values
          #show.ci = TRUE, # Show confidence intervals
          show.se = TRUE, # Show standard errors
          title = "Combined Mixed-Effects Model Results")

#tab_model(m6)
#tbl_regression(m1) %>% as_gt()
#summary(m1)
```

```{r}
m7 <- lmer(scale(change) ~ scale(RSE) + scale(outdegree) + (scale(RSE) * scale(outdegree)) + (scale(outdegree) | loginID), data=all)
m72 <- lmer(scale(change) ~ scale(NFC) + scale(outdegree) + (scale(NFC) * scale(outdegree)) + (scale(outdegree) | loginID), data=all)
m73 <- lmer(scale(change) ~ scale(SCC) + scale(outdegree) + (scale(SCC) * scale(outdegree)) + (scale(outdegree) | loginID), data=all)
m74 <- lmer(scale(change) ~ scale(DSS) + scale(outdegree) + (scale(DSS) * scale(outdegree)) + (scale(outdegree) | loginID), data=all)
m75 <- lmer(scale(change) ~ scale(CESD) + scale(outdegree) + (scale(CESD) * scale(outdegree)) + (scale(outdegree) | loginID), data=all)
m76 <- lmer(scale(change) ~ scale(SHS) + scale(outdegree) + (scale(SHS) * scale(outdegree)) + (scale(outdegree) | loginID), data=all)
m77 <- lmer(scale(change) ~ scale(Ref_mean) + scale(outdegree) + (scale(Ref_mean) * scale(outdegree)) + (scale(outdegree) | loginID), data=all)
m78 <- lmer(scale(change) ~ scale(Rum_mean) + scale(outdegree) + (scale(Rum_mean) * scale(outdegree)) + (scale(outdegree) | loginID), data=all)

tab_model(m7, m72, m73, m74, 
          show.p = TRUE,  # Show p-values
          #show.ci = TRUE, # Show confidence intervals
          show.se = TRUE, # Show standard errors
          title = "Combined Mixed-Effects Model Results")

tab_model(m75, m76, m77, m78, 
          show.p = TRUE,  # Show p-values
          #show.ci = TRUE, # Show confidence intervals
          show.se = TRUE, # Show standard errors
          title = "Combined Mixed-Effects Model Results")


#tab_model(m7)
#tbl_regression(m1) %>% as_gt()
#summary(m1)
```

```{r}

m8 <- lmer(scale(recency_sum) ~ scale(RSE) + scale(outdegree) + (scale(RSE) * scale(outdegree)) + (scale(outdegree) | loginID), data=all)
m82 <- lmer(scale(recency_sum) ~ scale(NFC) + scale(outdegree) + (scale(NFC) * scale(outdegree)) + (scale(outdegree) | loginID), data=all)
m83 <- lmer(scale(recency_sum) ~ scale(SCC) + scale(outdegree) + (scale(SCC) * scale(outdegree)) + (scale(outdegree) | loginID), data=all)
m84 <- lmer(scale(recency_sum) ~ scale(DSS) + scale(outdegree) + (scale(DSS) * scale(outdegree)) + (scale(outdegree) | loginID), data=all)
m85 <- lmer(scale(recency_sum) ~ scale(CESD) + scale(outdegree) + (scale(CESD) * scale(outdegree)) + (scale(outdegree) | loginID), data=all)
m86 <- lmer(scale(recency_sum) ~ scale(SHS) + scale(outdegree) + (scale(SHS) * scale(outdegree)) + (scale(outdegree) | loginID), data=all)
m87 <- lmer(scale(recency_sum) ~ scale(Ref_mean) + scale(outdegree) + (scale(Ref_mean) * scale(outdegree)) + (scale(outdegree) | loginID), data=all)

m88 <- lmer(scale(recency_sum) ~ scale(Rum_mean) + scale(outdegree) + (scale(Rum_mean) * scale(outdegree)) + (scale(outdegree) | loginID), data=all)
summary(m88)
tab_model(m88)
recentRum_r2 <- partR2(m88)

tab_model(m8, m82, m83, m84, 
          show.p = TRUE,  # Show p-values
          #show.ci = TRUE, # Show confidence intervals
          show.se = TRUE, # Show standard errors
          title = "Combined Mixed-Effects Model Results")

tab_model(m85, m86, m87, m88, 
          show.p = TRUE,  # Show p-values
          #show.ci = TRUE, # Show confidence intervals
          show.se = TRUE, # Show standard errors
          title = "Combined Mixed-Effects Model Results")

#tab_model(m8)
#tbl_regression(m1) %>% as_gt()
#summary(m1)
```


# Grouping outdegree based on high/low
```{r}
all$outdegree <- as.numeric(all$outdegree)

all <- all %>%
  mutate(median = median(outdegree, na.rm = TRUE),
         outdegree_groups = case_when(
           outdegree > median ~ "High Outdegree",
           outdegree < median ~ "Low Outdegree",
           TRUE ~ "Medium Outdegree" 
         ))

```

# Grouping self-esteem based on high/low
```{r}
all$RSE <- RSE$RSE

all <- all %>%
  mutate(median = median(RSE, na.rm = TRUE),
         RSE_groups = case_when(
           RSE > median ~ "High Self-Esteem",
           RSE < median ~ "Low Self-Esteem",
           TRUE ~ "Medium Self-Esteem"
         ))

freq_table <- all %>%
  count(RSE_groups)
```



# Visualizing significant outdegree x individual differences models
```{r}
m3 <- lmer(scale(importance) ~ scale(RSE) + scale(outdegree) + (scale(RSE) * scale(outdegree)) + (scale(outdegree) | loginID), data=all)
tab_model(m3) # Memory importance depends on an interaction between self-esteem and outdegree centrality

importance_plot <- ggplot(all, aes(x = RSE, y = importance, color = outdegree_groups)) +
  geom_smooth(method = "lm", se = TRUE, alpha = 0.2, level = 0.95, na.rm = TRUE) +
  labs(x = "Self-Esteem",
       y = "Percieved Personal Importance",
       color = "Levels of Outdegree Centrality") +
  theme_minimal() +
  theme(
    axis.title.x = element_text(face = "bold"),   # Make x-axis label bold
    axis.title.y = element_text(face = "bold"),   # Make y-axis label bold
    panel.grid.major = element_blank(),          # Remove major gridlines
    scale_color_manual(values = c("High Outdegree" = "blue",
                                  "Medium Outdegree" = "gold",
                                  "Low Outdegree" = "black"))
  )
plot(importance_plot)


# importance_plot <- ggplot(all %>% filter(!is.na(RSE_groups)), 
#                           aes(x = outdegree, y = importance, color = RSE_groups)) +
#   geom_smooth(method = "lm", se = TRUE, alpha = 0.2, level = 0.95, na.rm = TRUE) +
#   labs(x = "Outdegree Centrality",
#        y = "Perceived Personal Importance",
#        color = "Levels of Self-Esteem") +
#   theme_minimal() +
#   theme(
#     axis.title.x = element_text(face = "bold"),   # Make x-axis label bold
#     axis.title.y = element_text(face = "bold"),   # Make y-axis label bold
#     panel.grid.major = element_blank(),            # Remove major gridlines
#     legend.position = "top",
#     legend.direction = "horizontal"  
#   ) + 
#   coord_cartesian(xlim = c(min(all$outdegree, na.rm = TRUE), 
#                            max(all$outdegree, na.rm = TRUE))) +
#    scale_color_manual(values = c("High Self-Esteem" = "blue",
#                                "Low Self-Esteem" = "gold",
#                                "Medium Self-Esteem" = "black"))
# plot(importance_plot)
# importanceRSE_r2 <- partR2(m3)

m47 <- lmer(scale(clear) ~ scale(Ref_mean) + scale(outdegree) + (scale(Ref_mean) * scale(outdegree)) + (scale(outdegree) | loginID), data=all)
tab_model(m47) # Reflection tendencies and outdegree together predict clarity of memory recall

clear_plot <- ggplot(all, aes(x = Ref_mean, y = clear, color = outdegree_groups)) +
  geom_smooth(method = "lm", se = TRUE, alpha = 0.2, level = 0.95) +
  labs(title = "Predicted Effects of Reflection and Outdegree Centrality on Memory Clarity",
       x = "Reflection",
       y = "Memory Clarity",
       color = "Levels of Outdegree Centrality") +
  theme_minimal() +
  theme(
    axis.title.x = element_text(face = "bold"),   # Make x-axis label bold
    axis.title.y = element_text(face = "bold"),   # Make y-axis label bold
    panel.grid.major = element_blank(),            # Remove major gridlines
    )
plot(clear_plot)

m53 <- lmer(scale(easy) ~ scale(SCC) + scale(outdegree) + (scale(SCC) * scale(outdegree)) + (scale(outdegree) | loginID), data=all)
tab_model(m53) # outdegree is a significant predictor of ease of recall in a model accounting for self-concept clarity
# ease_plot <- ggplot(all, aes(x = outdegree, y = easy)) +
#   geom_smooth(method = "lm", se = TRUE, alpha = 0.2, level = 0.95) +
#   labs(title = "Predicted Effects of Reflection and Outdegree Centrality on Memory Clarity",
#        x = "Outdegree Centrality",
#        y = "Memory Ease of Recall") +
#   theme_minimal() +
#   theme(
#     axis.title.x = element_text(face = "bold"),   # Make x-axis label bold
#     axis.title.y = element_text(face = "bold"),   # Make y-axis label bold
#     panel.grid.major = element_blank()            # Remove major gridlines
#   )
# plot(ease_plot)

m66 <- lmer(scale(agency) ~ scale(SHS) + scale(outdegree) + (scale(SHS) * scale(outdegree)) + (scale(outdegree) | loginID), data=all)
tab_model(m66) # outdegree is a significant predictor of agency in a model accounting for subjective happiness

m8 <- lmer(scale(recency_sum) ~ scale(RSE) + scale(outdegree) + (scale(RSE) * scale(outdegree)) + (scale(outdegree) | loginID), data=all)
tab_model(m8) # outdegree is a significant predictor of recency (in days) in a model accounting for self-esteem

m82 <- lmer(scale(recency_sum) ~ scale(NFC) + scale(outdegree) + (scale(NFC) * scale(outdegree)) + (scale(outdegree) | loginID), data=all)
tab_model(m82) # outdegree is a significant predictor of recency in a model accounting for need for cognition

m83 <- lmer(scale(recency_sum) ~ scale(SCC) + scale(outdegree) + (scale(SCC) * scale(outdegree)) + (scale(outdegree) | loginID), data=all)
tab_model(m83) # outdegree is a significant predictor of recency in a model accounting for self-concept clarity

m85 <- lmer(scale(recency_sum) ~ scale(CESD) + scale(outdegree) + (scale(CESD) * scale(outdegree)) + (scale(outdegree) | loginID), data=all)
tab_model(m85) # depressive symptoms are a significant predictor of recency in a model accounting for outdegree centrality

m87 <- lmer(scale(recency_sum) ~ scale(Ref_mean) + scale(outdegree) + (scale(Ref_mean) * scale(outdegree)) + (scale(outdegree) | loginID), data=all)
tab_model(m87) # outdegree is a significant predictor of recency in a model accounting for reflection

m88 <- lmer(scale(recency_sum) ~ scale(Rum_mean) + scale(outdegree) + (scale(Rum_mean) * scale(outdegree)) + (scale(outdegree) | loginID), data=all)
tab_model(m88) # Both rumination and outdegree predict recency, but not the interaction between the two
```





















# Predicting memory RATINGS from INDEGREE x individual differences
```{r}

m10 <- lmer(scale(transformativeness) ~ scale(RSE) + scale(indegree) + (scale(RSE) * scale(indegree)) + (scale(indegree) | loginID), data=all)
#tab_model(m10)
m102 <- lmer(scale(transformativeness) ~ scale(NFC) + scale(indegree) + (scale(NFC) * scale(indegree)) + (scale(indegree) | loginID), data=all)
m103 <- lmer(scale(transformativeness) ~ scale(SCC) + scale(indegree) + (scale(SCC) * scale(indegree)) + (scale(indegree) | loginID), data=all)
#tab_model(m103)
m104 <- lmer(scale(transformativeness) ~ scale(DSS) + scale(indegree) + (scale(DSS) * scale(indegree)) + (scale(indegree) | loginID), data=all)
m105 <- lmer(scale(transformativeness) ~ scale(CESD) + scale(indegree) + (scale(CESD) * scale(indegree)) + (scale(indegree) | loginID), data=all)
m106 <- lmer(scale(transformativeness) ~ scale(SHS) + scale(indegree) + (scale(SHS) * scale(indegree)) + (scale(indegree) | loginID), data=all)
m107 <- lmer(scale(transformativeness) ~ scale(Ref_mean) + scale(indegree) + (scale(Ref_mean) * scale(indegree)) + (scale(indegree) | loginID), data=all)
m108 <- lmer(scale(transformativeness) ~ scale(Rum_mean) + scale(indegree) + (scale(Rum_mean) * scale(indegree)) + (scale(indegree) | loginID), data=all)

tab_model(m10, m102, m103, m104, 
          show.p = TRUE,  # Show p-values
          #show.ci = TRUE, # Show confidence intervals
          show.se = TRUE, # Show standard errors
          title = "Combined Mixed-Effects Model Results")

tab_model(m105, m106, m107, m108, 
          show.p = TRUE,  # Show p-values
          #show.ci = TRUE, # Show confidence intervals
          show.se = TRUE, # Show standard errors
          title = "Combined Mixed-Effects Model Results")

#tbl_regression(m1) %>% as_gt()
#summary(m1)
```

```{r}
m20 <- lmer(scale(valRate) ~ scale(RSE) + scale(indegree) + (scale(RSE) * scale(indegree)) + (scale(indegree) | loginID), data=all)
m201 <- lmer(scale(valRate) ~ scale(NFC) + scale(indegree) + (scale(NFC) * scale(indegree)) + (scale(indegree) | loginID), data=all)
m202 <- lmer(scale(valRate) ~ scale(SCC) + scale(indegree) + (scale(SCC) * scale(indegree)) + (scale(indegree) | loginID), data=all)
m203 <- lmer(scale(valRate) ~ scale(DSS) + scale(indegree) + (scale(DSS) * scale(indegree)) + (scale(indegree) | loginID), data=all)
m204 <- lmer(scale(valRate) ~ scale(CESD) + scale(indegree) + (scale(CESD) * scale(indegree)) + (scale(indegree) | loginID), data=all)
tab_model(m204)
m205 <- lmer(scale(valRate) ~ scale(SHS) + scale(indegree) + (scale(SHS) * scale(indegree)) + (scale(indegree) | loginID), data=all)
m206 <- lmer(scale(valRate) ~ scale(Ref_mean) + scale(indegree) + (scale(Ref_mean) * scale(indegree)) + (scale(indegree) | loginID), data=all)
m207 <- lmer(scale(valRate) ~ scale(Rum_mean) + scale(indegree) + (scale(Rum_mean) * scale(indegree)) + (scale(indegree) | loginID), data=all)

tab_model(m20, m201, m202, m203, 
          show.p = TRUE,  # Show p-values
          #show.ci = TRUE, # Show confidence intervals
          show.se = TRUE, # Show standard errors
          title = "Combined Mixed-Effects Model Results")

tab_model(m204, m205, m206, m207, 
          show.p = TRUE,  # Show p-values
          #show.ci = TRUE, # Show confidence intervals
          show.se = TRUE, # Show standard errors
          title = "Combined Mixed-Effects Model Results")

#tab_model(m2)
#tbl_regression(m1) %>% as_gt()
#summary(m1)
```

```{r}

m30 <- lmer(scale(importance) ~ scale(RSE) + scale(indegree) + (scale(RSE) * scale(indegree)) + (scale(indegree) | loginID), data=all)
m302 <- lmer(scale(importance) ~ scale(NFC) + scale(indegree) + (scale(NFC) * scale(indegree)) + (scale(indegree) | loginID), data=all)
m303 <- lmer(scale(importance) ~ scale(SCC) + scale(indegree) + (scale(SCC) * scale(indegree)) + (scale(indegree) | loginID), data=all)
tab_model(m303)

m304 <- lmer(scale(importance) ~ scale(DSS) + scale(indegree) + (scale(DSS) * scale(indegree)) + (scale(indegree) | loginID), data=all)
m305 <- lmer(scale(importance) ~ scale(CESD) + scale(indegree) + (scale(CESD) * scale(indegree)) + (scale(indegree) | loginID), data=all)
m306 <- lmer(scale(importance) ~ scale(SHS) + scale(indegree) + (scale(SHS) * scale(indegree)) + (scale(indegree) | loginID), data=all)
tab_model(m306)

m307 <- lmer(scale(importance) ~ scale(Ref_mean) + scale(indegree) + (scale(Ref_mean) * scale(indegree)) + (scale(indegree) | loginID), data=all)
m308 <- lmer(scale(importance) ~ scale(Rum_mean) + scale(indegree) + (scale(Rum_mean) * scale(indegree)) + (scale(indegree) | loginID), data=all)

tab_model(m30, m302, m303, m304, 
          show.p = TRUE,  # Show p-values
          #show.ci = TRUE, # Show confidence intervals
          show.se = TRUE, # Show standard errors
          title = "Combined Mixed-Effects Model Results")

tab_model(m305, m306, m307, m308, 
          show.p = TRUE,  # Show p-values
          #show.ci = TRUE, # Show confidence intervals
          show.se = TRUE, # Show standard errors
          title = "Combined Mixed-Effects Model Results")

#tab_model(m3)
#tbl_regression(m1) %>% as_gt()
#summary(m1)
```

```{r}

m40 <- lmer(scale(clear) ~ scale(RSE) + scale(indegree) + (scale(RSE) * scale(indegree)) + (scale(indegree) | loginID), data=all)
m402 <- lmer(scale(clear) ~ scale(NFC) + scale(indegree) + (scale(NFC) * scale(indegree)) + (scale(indegree) | loginID), data=all)
m403 <- lmer(scale(clear) ~ scale(SCC) + scale(indegree) + (scale(SCC) * scale(indegree)) + (scale(indegree) | loginID), data=all)
m404 <- lmer(scale(clear) ~ scale(DSS) + scale(indegree) + (scale(DSS) * scale(indegree)) + (scale(indegree) | loginID), data=all)
m405 <- lmer(scale(clear) ~ scale(CESD) + scale(indegree) + (scale(CESD) * scale(indegree)) + (scale(indegree) | loginID), data=all)
m406 <- lmer(scale(clear) ~ scale(SHS) + scale(indegree) + (scale(SHS) * scale(indegree)) + (scale(indegree) | loginID), data=all)
m407 <- lmer(scale(clear) ~ scale(Ref_mean) + scale(indegree) + (scale(Ref_mean) * scale(indegree)) + (scale(indegree) | loginID), data=all)
m408 <- lmer(scale(clear) ~ scale(Rum_mean) + scale(indegree) + (scale(Rum_mean) * scale(indegree)) + (scale(indegree) | loginID), data=all)


tab_model(m40, m402, m403, m404, 
          show.p = TRUE,  # Show p-values
          #show.ci = TRUE, # Show confidence intervals
          show.se = TRUE, # Show standard errors
          title = "Combined Mixed-Effects Model Results")

tab_model(m405, m406, m407, m408, 
          show.p = TRUE,  # Show p-values
          #show.ci = TRUE, # Show confidence intervals
          show.se = TRUE, # Show standard errors
          title = "Combined Mixed-Effects Model Results")


#tab_model(m4)
#tbl_regression(m1) %>% as_gt()
#summary(m1)
```

```{r}
m50 <- lmer(scale(easy) ~ scale(RSE) + scale(indegree) + (scale(RSE) * scale(indegree)) + (scale(indegree) | loginID), data=all)
m502 <- lmer(scale(easy) ~ scale(NFC) + scale(indegree) + (scale(NFC) * scale(indegree)) + (scale(indegree) | loginID), data=all)
m503 <- lmer(scale(easy) ~ scale(SCC) + scale(indegree) + (scale(SCC) * scale(indegree)) + (scale(indegree) | loginID), data=all)
m504 <- lmer(scale(easy) ~ scale(DSS) + scale(indegree) + (scale(DSS) * scale(indegree)) + (scale(indegree) | loginID), data=all)
m505 <- lmer(scale(easy) ~ scale(CESD) + scale(indegree) + (scale(CESD) * scale(indegree)) + (scale(indegree) | loginID), data=all)
m506 <- lmer(scale(easy) ~ scale(SHS) + scale(indegree) + (scale(SHS) * scale(indegree)) + (scale(indegree) | loginID), data=all)
m507 <- lmer(scale(easy) ~ scale(Ref_mean) + scale(indegree) + (scale(Ref_mean) * scale(indegree)) + (scale(indegree) | loginID), data=all)
m508 <- lmer(scale(easy) ~ scale(Rum_mean) + scale(indegree) + (scale(Rum_mean) * scale(indegree)) + (scale(indegree) | loginID), data=all)

tab_model(m50, m502, m503, m504, 
          show.p = TRUE,  # Show p-values
          #show.ci = TRUE, # Show confidence intervals
          show.se = TRUE, # Show standard errors
          title = "Combined Mixed-Effects Model Results")

tab_model(m505, m506, m507, m508, 
          show.p = TRUE,  # Show p-values
          #show.ci = TRUE, # Show confidence intervals
          show.se = TRUE, # Show standard errors
          title = "Combined Mixed-Effects Model Results")

#tab_model(m5)
#tbl_regression(m1) %>% as_gt()
#summary(m1)
```

```{r}
m60 <- lmer(scale(agency) ~ scale(RSE) + scale(indegree) + (scale(RSE) * scale(indegree)) + (scale(indegree) | loginID), data=all)
m602 <- lmer(scale(agency) ~ scale(NFC) + scale(indegree) + (scale(NFC) * scale(indegree)) + (scale(indegree) | loginID), data=all)
m603 <- lmer(scale(agency) ~ scale(SCC) + scale(indegree) + (scale(SCC) * scale(indegree)) + (scale(indegree) | loginID), data=all)
m604 <- lmer(scale(agency) ~ scale(DSS) + scale(indegree) + (scale(DSS) * scale(indegree)) + (scale(indegree) | loginID), data=all)
m605 <- lmer(scale(agency) ~ scale(CESD) + scale(indegree) + (scale(CESD) * scale(indegree)) + (scale(indegree) | loginID), data=all)
m606 <- lmer(scale(agency) ~ scale(SHS) + scale(indegree) + (scale(SHS) * scale(indegree)) + (scale(indegree) | loginID), data=all)
m607 <- lmer(scale(agency) ~ scale(Ref_mean) + scale(indegree) + (scale(Ref_mean) * scale(indegree)) + (scale(indegree) | loginID), data=all)
m608 <- lmer(scale(agency) ~ scale(Rum_mean) + scale(indegree) + (scale(Rum_mean) * scale(indegree)) + (scale(indegree) | loginID), data=all)

tab_model(m60, m602, m603, m604, 
          show.p = TRUE,  # Show p-values
          #show.ci = TRUE, # Show confidence intervals
          show.se = TRUE, # Show standard errors
          title = "Combined Mixed-Effects Model Results")

tab_model(m605, m606, m607, m608, 
          show.p = TRUE,  # Show p-values
          #show.ci = TRUE, # Show confidence intervals
          show.se = TRUE, # Show standard errors
          title = "Combined Mixed-Effects Model Results")

#tab_model(m6)
#tbl_regression(m1) %>% as_gt()
#summary(m1)
```

```{r}
m70 <- lmer(scale(change) ~ scale(RSE) + scale(indegree) + (scale(RSE) * scale(indegree)) + (scale(indegree) | loginID), data=all)
m702 <- lmer(scale(change) ~ scale(NFC) + scale(indegree) + (scale(NFC) * scale(indegree)) + (scale(indegree) | loginID), data=all)
m703 <- lmer(scale(change) ~ scale(SCC) + scale(indegree) + (scale(SCC) * scale(indegree)) + (scale(indegree) | loginID), data=all)
tab_model(m703)

m704 <- lmer(scale(change) ~ scale(DSS) + scale(indegree) + (scale(DSS) * scale(indegree)) + (scale(indegree) | loginID), data=all)
m705 <- lmer(scale(change) ~ scale(CESD) + scale(indegree) + (scale(CESD) * scale(indegree)) + (scale(indegree) | loginID), data=all)
m706 <- lmer(scale(change) ~ scale(SHS) + scale(indegree) + (scale(SHS) * scale(indegree)) + (scale(indegree) | loginID), data=all)
m707 <- lmer(scale(change) ~ scale(Ref_mean) + scale(indegree) + (scale(Ref_mean) * scale(indegree)) + (scale(indegree) | loginID), data=all)
m708 <- lmer(scale(change) ~ scale(Rum_mean) + scale(indegree) + (scale(Rum_mean) * scale(indegree)) + (scale(indegree) | loginID), data=all)
tab_model(m708)

tab_model(m70, m702, m703, m704, 
          show.p = TRUE,  # Show p-values
          #show.ci = TRUE, # Show confidence intervals
          show.se = TRUE, # Show standard errors
          title = "Combined Mixed-Effects Model Results")

tab_model(m705, m706, m707, m708, 
          show.p = TRUE,  # Show p-values
          #show.ci = TRUE, # Show confidence intervals
          show.se = TRUE, # Show standard errors
          title = "Combined Mixed-Effects Model Results")


#tab_model(m7)
#tbl_regression(m1) %>% as_gt()
#summary(m1)
```

```{r}

m80 <- lmer(scale(recency_sum) ~ scale(RSE) + scale(indegree) + (scale(RSE) * scale(indegree)) + (scale(indegree) | loginID), data=all)
m802 <- lmer(scale(recency_sum) ~ scale(NFC) + scale(indegree) + (scale(NFC) * scale(indegree)) + (scale(indegree) | loginID), data=all)
m803 <- lmer(scale(recency_sum) ~ scale(SCC) + scale(indegree) + (scale(SCC) * scale(indegree)) + (scale(indegree) | loginID), data=all)
m804 <- lmer(scale(recency_sum) ~ scale(DSS) + scale(indegree) + (scale(DSS) * scale(indegree)) + (scale(indegree) | loginID), data=all)
m805 <- lmer(scale(recency_sum) ~ scale(CESD) + scale(indegree) + (scale(CESD) * scale(indegree)) + (scale(indegree) | loginID), data=all)
m806 <- lmer(scale(recency_sum) ~ scale(SHS) + scale(indegree) + (scale(SHS) * scale(indegree)) + (scale(indegree) | loginID), data=all)
m807 <- lmer(scale(recency_sum) ~ scale(Ref_mean) + scale(indegree) + (scale(Ref_mean) * scale(indegree)) + (scale(indegree) | loginID), data=all)
m808 <- lmer(scale(recency_sum) ~ scale(Rum_mean) + scale(indegree) + (scale(Rum_mean) * scale(indegree)) + (scale(indegree) | loginID), data=all)
tab_model(m808)

tab_model(m80, m802, m803, m804, 
          show.p = TRUE,  # Show p-values
          #show.ci = TRUE, # Show confidence intervals
          show.se = TRUE, # Show standard errors
          title = "Combined Mixed-Effects Model Results")

tab_model(m805, m806, m807, m808, 
          show.p = TRUE,  # Show p-values
          #show.ci = TRUE, # Show confidence intervals
          show.se = TRUE, # Show standard errors
          title = "Combined Mixed-Effects Model Results")

#tab_model(m8)
#tbl_regression(m1) %>% as_gt()
#summary(m1)
```





```{r}
# Define the function to fit lmer models with two regressors, interaction term, and random effects
calculate_lmer_models_interaction <- function(data, models_info, random_effect) {
  results <- list()  # Initialize an empty list to store model results
  
  # Function to format p-values with asterisks
  format_p_value <- function(p) {
    if (p < 0.001) {
      return(paste0(format(round(p, 3), scientific = FALSE), "***"))
    } else if (p < 0.01) {
      return(paste0(format(round(p, 3), scientific = FALSE), "**"))
    } else if (p < 0.05) {
      return(paste0(format(round(p, 3), scientific = FALSE), "*"))
    } else {
      return(format(round(p, 3), scientific = FALSE))
    }
  }
  
  # Loop over each model specification
  for (i in 1:nrow(models_info)) {
    outcome <- models_info[i, 1]   # Outcome variable
    regressor1 <- models_info[i, 2] # First regressor
    regressor2 <- models_info[i, 3] # Second regressor
    interaction_term <- paste(regressor1, "*", regressor2) # Interaction term
    
    # Scale the predictors within the data
    data[[regressor1]] <- scale(data[[regressor1]])
    data[[regressor2]] <- scale(data[[regressor2]])
    
    # Construct the formula for lmer
    formula <- as.formula(paste(outcome, "~", regressor1, "+", regressor2, "+", 
                                interaction_term, "+ (1 +", random_slope_predictor, "|", random_effect, ")"))
    
    # Fit the lmer model
    model <- lmer(formula, data = data)
    
    # Use broom.mixed::tidy() to extract the model statistics
    model_summary <- tidy(model, effects = "fixed", conf.int = TRUE)
    
    # Add the model specification to the summary
    model_summary <- model_summary %>%
      mutate(Outcome = outcome, Predictor1 = regressor1, Predictor2 = regressor2) %>%
      mutate(p.value = sapply(p.value, format_p_value)) %>%
      select(Outcome, Predictor1, Predictor2, term, estimate, std.error, conf.low, conf.high, p.value)
    
    # Store the results in the list
    results[[i]] <- model_summary
  }
  
  # Combine all model summaries into a single dataframe
  results_df <- bind_rows(results)
  
  return(results_df)
}
```

# Outdegree multiple regression visualization
```{r}
# Define the outcome and predictors (two regressors and interaction term) for the models
models_info <- data.frame(
  Outcome = c("transformativeness", "valRate", "importance","clear","easy","agency","change","recency_sum"),
  Regressor1 = c("RSE","NFC","SCC","DSS","CESD","SHS","Ref_mean","Rum_mean"),
  Regressor2 = c("outdegree") # Here it's Days vs Days, but can be different variables
)

# Specify the random effect (grouping variable)
random_effect <- "loginID"
random_slope_predictor <- "outdegree"

# Fit the lmer models and extract summary statistics
lmer_results_interaction <- calculate_lmer_models_interaction(all, models_info, random_effect)

# View the results
print(lmer_results_interaction)

kable(lmer_results_interaction)

# Create a styled table with kableExtra
kable(lmer_results_interaction, caption = "Ind. Differences and Outdegree Predicting Memory Ratings") %>%
  kable_styling(full_width = FALSE, position = "center") %>%
  column_spec(1, bold = TRUE) %>%
  column_spec(2:4, color = "blue")
```


# Predicting memory RATINGS from indegree x individual differences
```{r}
m1 <- lmer(scale(transformativeness) ~ scale(Ref_mean) + scale(indegree) + (scale(Ref_mean) * scale(indegree)) + (scale(indegree) | loginID), data=all)
tab_model(m1)

#tbl_regression(m1) %>% as_gt()
#summary(m1)
```

```{r}
m2 <- lmer(scale(valRate) ~ scale(RSE) + scale(indegree) + (scale(RSE) * scale(indegree)) + (scale(indegree) | loginID), data=all)
tab_model(m2)

#tbl_regression(m1) %>% as_gt()
#summary(m1)
```

```{r}
m3 <- lmer(scale(importance) ~ scale(Rum_mean) + scale(indegree) + (scale(Rum_mean) * scale(indegree)) + (scale(indegree) | loginID), data=all)
tab_model(m3)

#tbl_regression(m1) %>% as_gt()
#summary(m1)
```

```{r}
m4 <- lmer(scale(clear) ~ scale(Rum_mean) + scale(indegree) + (scale(Rum_mean) * scale(indegree)) + (scale(indegree) | loginID), data=all)
tab_model(m4)

#tbl_regression(m1) %>% as_gt()
#summary(m1)
```

```{r}
m5 <- lmer(scale(easy) ~ scale(Rum_mean) + scale(indegree) + (scale(Rum_mean) * scale(indegree)) + (scale(indegree) | loginID), data=all)
tab_model(m5)

#tbl_regression(m1) %>% as_gt()
#summary(m1)
```

```{r}
m6 <- lmer(scale(agency) ~ scale(Rum_mean) + scale(indegree) + (scale(Rum_mean) * scale(indegree)) + (scale(indegree) | loginID), data=all)
tab_model(m6)

#tbl_regression(m1) %>% as_gt()
#summary(m1)
```

```{r}
m7 <- lmer(scale(change) ~ scale(Rum_mean) + scale(indegree) + (scale(Rum_mean) * scale(indegree)) + (scale(indegree) | loginID), data=all)
tab_model(m7)

#tbl_regression(m1) %>% as_gt()
#summary(m1)
```

```{r}
m8 <- lmer(scale(recency_sum) ~ scale(Rum_mean) + scale(indegree) + (scale(Rum_mean) * scale(indegree)) + (scale(indegree) | loginID), data=all)
tab_model(m8)

#tbl_regression(m1) %>% as_gt()
#summary(m1)
```


##############################################################################
##############################################################################
##############################################################################


##  Predicting individual differences from network density

```{r}
# Remove subj2 - lack of density values? N = 46 (excluding 22 and 2 from centrality analyses)
data <- data[data$loginID != 2, ]

# dens <- read_csv("densityDf.csv")
# dens <- dens[ ,-c(1,2)]

# dense <- dense[-c(1:23), , drop = FALSE]

#denseModel <- cbind(iDiffs,dens)
#denseModel<- denseModel[!duplicated(denseModel$loginID), ]
```
```{r}
# Define the function to calculate correlations using cor.test
calculate_correlations_cortest <- function(data, var_pairs) {
  results <- list()  # Initialize an empty list to store correlation results
  
  # Loop over each pair of variables
  for (i in 1:nrow(var_pairs)) {
    var1 <- var_pairs[i, 1]
    var2 <- var_pairs[i, 2]
    
    # Calculate correlation using cor.test
    cor_test <- cor.test(data[[var1]], data[[var2]])
    
    # Extract correlation value, p-value, and confidence intervals
    cor_value <- cor_test$estimate
    p_value <- cor_test$p.value
    ci_lower <- cor_test$conf.int[1]
    ci_upper <- cor_test$conf.int[2]
    
    # Store results in a list
    results[[i]] <- data.frame(
      Variable1 = var1,
      Variable2 = var2,
      Correlation = round(cor_value, 3),
      P_value = round(p_value, 3),
      CI_Lower = round(ci_lower, 3),
      CI_Upper = round(ci_upper, 3)
    )
  }
  
  # Combine results into a single dataframe
  results_df <- bind_rows(results)
  
  return(results_df)
}
```


```{r}
# Does centrality predict RSE?
#RSE_dens <-lmer( scale(RSE) ~ scale(dense) + ( scale(dense) | loginID), data=data)

#m10 <-lm( scale(transformativeness) ~ scale(RSE) + scale(dense) + (scale(CESD) + scale(dense)), data=all)

m10 <- cor.test(scale(all$dense),scale(all$RSE),method = "pearson") ##
tab_model(m10)

m11 <- cor.test(scale(all$dense),scale(all$NFC),method = "pearson")
tab_model(m11)

m12 <- cor.test(scale(all$dense),scale(all$SCC),method = "pearson")
tab_model(m12)

m13 <- cor.test(scale(all$dense),scale(all$DSS),method = "pearson") ##
tab_model(m13)

m14 <- cor.test(scale(all$dense),scale(all$CESD),method = "pearson") ##
tab_model(m14)

m15 <- cor.test(scale(all$dense),scale(all$SHS),method = "pearson") ##
tab_model(m15)

m16 <- cor.test(scale(all$dense),scale(all$Ref_mean),method = "pearson")
tab_model(m16)

m17 <- cor.test(scale(all$dense),scale(all$Rum_mean),method = "pearson") ##
tab_model(m17)

var_pairs <- data.frame(
  Density = c("dense"),
  IndDiff = c("RSE", "NFC", "SCC","DSS","CESD","SHS","Ref_mean","Rum_mean")
)

correlation_results <- calculate_correlations_cortest(all,var_pairs)
print(correlation_results)

#library(knitr)
 
# kable(correlation_results, 
#       caption = "Correlation Results with Confidence Intervals",
#       )

kable(correlation_results, caption = "Correlations between network density and individual differences measures") %>%
  kable_styling(full_width = FALSE, position = "center") %>%
  column_spec(1, bold = TRUE) %>%
  column_spec(2:4, color = "blue")

#report(m10)
#tab_model(m10)
```

# Memory Maps Extension Power Analysis
```{r}
if (!require("devtools")) {
  install.packages("devtools", dependencies = TRUE)}

devtools::install_github("DejanDraschkow/mixedpower")
library(mixedpower)

all <- all %>%
  mutate(RSE_scaled = scale(RSE, center = TRUE, scale = TRUE))
##############################################################################
# Model 1 - outdegree and self-esteem on personal importance

#Fill in NAs for self-esteem using mean imputation
all$RSE_scaled[is.na(all$RSE_scaled)] <- mean(all$RSE_scaled, na.rm = TRUE)

# Base power analysis on self-esteem x transformativeness / personal importance finding from SYP
# model1 <- lmer(importance ~ outdegree_scaled * RSE + (outdegree_scaled | loginID), data = all)
model1_simple <- lmer(importance ~ outdegree_scaled * RSE_scaled + (outdegree_scaled | loginID), data = all)
summary(model1_simple)
df1 <- summary(model1)$coefficients[, "df"]

# Critical t-value for outdegree effects on personal importance
qt(p = 0.01, df = 42) # -2.41847 = -2.42

# Critical t-value for RSE effects on personal importance
qt(p = 0.01, df = 33) # -2.444794 = -2.44

# Critical t-value for interaction effects on personal importance
qt(p = 0.01, df = 44) # -2.414134 = -2.41

# Average of these critical t-values are -2.42

##############################################################################

model <- model1_simple # which model do we want to simulate power for?
data <- all # data used to fit the model
# fixed_effects <- c("outdegree", "RSE") # all fixed effects specified
fixed_effects <- c("outdegree_scaled","RSE_scaled")
simvar <- "loginID" # which random effect do we want to vary in the simulation?
steps <- c(80, 100, 120, 140) # which sample sizes do we want to look at?
critical_value <- 2.42 # which t/z value do we want to use to test for significance?
n_sim <- 1000 # how many single simulations should be used to estimate power?

# library(simr)
# power_model1_ext <- extend(model1_simple, along="loginID", n = 80) #extend data set to include 60 participants
# 
# powerC_model1 <- powerCurve(fit = power_model1, test = fixed(c("outdegree_scaled","RSE_scaled")), along = "loginID",
#                       breaks = c(60, 80, 100, 120))
# print(powerC_model1)

power_model1 <- mixedpower(model1_simple, data,fixed_effects,
                        simvar, steps,
                        critical_value, n_sim)
power_model1
multiplotPower(power_model1, ppi = 300, filename = "power.png")

##############################################################################
# Model 2 - outdegree and self-esteem on transformativeness

model2_simple <- lmer(transformativeness ~ outdegree_scaled * RSE + (outdegree_scaled | loginID), data = all)
summary(model2_simple)
df2 <- summary(model2_simple)$coefficients[, "df"]

# Same critical t-values as before 

model <- model2_simple # which model do we want to simulate power for?
data <- all # data used to fit the model
# fixed_effects <- c("outdegree", "RSE") # all fixed effects specified in FLPmodel
fixed_effects <- c("outdegree")
simvar <- "loginID" # which random effect do we want to vary in the simulation?
steps <- c(80, 100, 120, 140) # which sample sizes do we want to look at?
critical_value <- 2.42 # which t/z value do we want to use to test for significance?
n_sim <- 1000 # how many single simulations should be used to estimate power?

power_model1 <- mixedpower(model, data,fixed_effects,
                        simvar, steps,
                        critical_value, n_sim)
power_model1
multiplotPower(power_model1, ppi = 300, filename = "power.png")
```

