---
title: "R Notebook"
output: html_notebook
---

## Prepare for Analysis and Visualizations

```{r}
#library(groundhog)

pkgs <-  c("tidyverse","here", "lmerTest", "sjPlot","broom.mixed", "kableExtra", "ggeffects", "gt", "brms", "bayestestR","ggdist", "pheatmap", "heatmaply","pheatmap","gplots","RColorBrewer", "tm", "wordcloud", "psych", "wesanderson","patchwork", "broom.mixed", "dplyr", "gtsummary")

pacman::p_load("tidyverse","here", "lmerTest", "sjPlot","broom.mixed", "kableExtra", "ggeffects", "gt", "brms", "bayestestR","ggdist", "pheatmap", "heatmaply","pheatmap","gplots","RColorBrewer", "tm", "wordcloud", "psych", "wesanderson","patchwork", "broom.mixed", "dplyr", "gtsummary","ordinal","r2glmm")

update.packages(pkgs)

library(lmerTest)
library(partR2)
library(dplyr)

# Useful resources Jake imported from S2 analysis
devtools::source_url("https://raw.githubusercontent.com/JacobElder/MiscellaneousR/master/corToOne.R")
devtools::source_url("https://raw.githubusercontent.com/JacobElder/MiscellaneousR/master/plotCommAxes.R")
devtools::source_url("https://raw.githubusercontent.com/JacobElder/MiscellaneousR/master/named.effects.ref.R")

# Import fullLong includes memories for each subject
fullLong <- read.csv("~/GitLab/SecondYearProject/MemoryMaps/Data/processed/fullLong48.csv")
fullLong <- fullLong[-1, ]

# Import fullShort - doesn't include memories for each subject
fullShort <- read.csv("~/GitLab/SecondYearProject/MemoryMaps/Data/processed/fullShort48.csv")
#fullShort <- fullShort[-1, ]
# rankData <- arrow::read_parquet(here("RepData/rankings2.parquet"))

# Join fullLong and fullShort
fullData <- fullLong %>% full_join(fullShort, by = c("subID"))
fullData$subID <- as.factor(fullData$subID)
# fullData <- fullData[ ,-1]

# Download fullData file for separate analysis (onset file creation)
write.csv(fullData,"~/GitLab/SecondYearProject/MemoryMaps/Data/processed/fullData48.csv")

# pal1 <-n colorRampPalette(brewer.pal(11,"BrBG"))(227)
pal <- colorRampPalette(wes_palette("Zissou1", 5))(length(unique(fullLong$subID)))

ID <- read.csv("ID_48.csv")
ID <- ID[,-c(1)]

```

# Linear Mixed Models (and some descriptives)

--------------------------------------------------------------------------------

# Centrality Predictors (A priori)

## From rep pipeline: valence (pos/neg) \~ degree centrality

### NOTE: this data was not collected through memory ratings, but were collected

### from the subject in the scanner.

```{r}
# m <- lmer(scale(positive) ~  scale(outdegree) + scale(indegree) + numID + ( scale(outdegree) + scale(indegree) | subID), data=fullData)
# 
# tbl_regression(m) %>% as_gt()
# # Indegree (counterfactually-central, such that other memories would not have happened without the target memory) memories closely predict self-reported positivity of memories)
# 
# m <-lmer( scale(vad_pos) ~  scale(strengthOut) + scale(strengthIn) + numID + ( scale(strengthOut) + scale(strengthIn) | subID), data=fullData)
# 
# tbl_regression(m) %>% as_gt()
# ```
# 
# ```{r}
# m<-lmer( scale(negative) ~  scale(outdegree) + scale(indegree) + numID + ( scale(outdegree) + scale(indegree) | subID), data=fullData)
# 
# tbl_regression(m) %>% as_gt()
# #
# ```
# 
# ```{r}
# m<-lmer( scale(vad_pos) ~  scale(outdegree) + scale(indegree) + numID + ( scale(outdegree) + scale(indegree) | subID), data=fullData)
# tbl_regression(m) %>% as_gt()
# r2beta(m)
# ```
# 
# ```{r}
# m<-lmer( scale(vad_pos) ~  scale(strengthOut) + scale(strengthIn) + numID + scale(length) + ( scale(strengthOut) + scale(strengthIn) | subID), data=fullData)
# tbl_regression(m) %>% as_gt()
```

## Centrality Descriptives - ACROSS Subjects

```{r}
cent <- fullData[, c(1,4,5,6)] # For descriptives and later onset file usage

degree_mean <- mean(cent$degree) # Average overall connections across networks
degree_sd <- sd(cent$degree) # Standard deviation of overall connections across networks
degree_freq <- hist(cent$degree) # Distribution of network density across subject networks
cent$degree_scaled <- as.vector(scale(cent$degree)) # Scaled density values for lme

outdegree_mean <- mean(cent$outdegree) # Average outward connections
outdegree_sd <- sd(cent$outdegree) # Standard deviation from average outward connections
outdegree_freq <- hist(cent$outdegree) # Distribution of network density across subject networks
cent$outdegree_scaled <- as.vector(scale(cent$outdegree)) # Scaled density values for lme

indegree_mean <- mean(cent$indegree) # Average inward connections
indegree_sd <- sd(cent$indegree) # Standard deviation from average outward connections
indegree_freq <- hist(cent$indegree) # Distribution of network density across subject networks
cent$indegree_scaled<- as.vector(scale(cent$indegree)) # Scaled density values for lme

write.csv(cent,"centralityDf_48.csv") # Write file to csv for later onset files
```

## Centrality Descriptives - WITHIN Subjects

```{r}
# Create subject list for descriptives loop
sublist <- as.array(unique(fullData$subID))

# Create dataframe to add to later and rename first column
withinDesc <- data.frame(unique(fullData$subID))
names(withinDesc)[1] <- "subID"

# Begin within-subjects loop
for (s in sublist){
  
  # Initialize df for current subject
  centsub <- cent %>%
    filter(subID == s)
  
  # Within-subject degree
  sub_degree1 <- round(mean(centsub$degree),5)
  sub_degree2 <- round(sd(centsub$degree),5)
  
  # Within-subject outdegree
  sub_outdegree1 <- round(mean(centsub$outdegree),5)
  sub_outdegree2 <- round(sd(centsub$outdegree),5)
  
  # Within-subject indegree
  sub_indegree1 <- round(mean(centsub$indegree),5)
  sub_indegree2 <- round(sd(centsub$indegree),5)
  
  withinDesc[ , 2:7] <- c(sub_degree1,sub_degree2,sub_outdegree1,sub_outdegree2,
                          sub_indegree1,sub_indegree2)
  
  names(withinDesc)[2:7] <- c("mean_degree","sd_degree","mean_outdegree","sd_outdegree",
                          "mean_indegree","sd_indegree")
  
}

write.csv(withinDesc,"withinDesc_48.csv") # Write file to csv for later onset files
```

## What happens if we remove the 6 subjects (of N=37 batch) that have an average degree less than 1. 
```{r}
# remove_subs <- c(17,24,46,79,90,108)
# 
# # Remove columns where the factor column matches the specified levels
# fullData2 <- fullData[!fullData$subID %in% remove_subs, ]
```

##################################################################


## Does directional degree centrality predict memory IMPORTANCE?

\>\>\>

```{r}
m <-lmer( scale(importance) ~  scale(outdegree) + scale(indegree) + numID + ( scale(outdegree) + scale(indegree) | subID), data=fullData) 

tbl_regression(m) %>% as_gt()


# Personal importance of the memory is equally associated with outdegree and indegree within the memory network

# StrengthIn/Out analyses from rep pipeline
# m<-lmer( scale(importance) ~  scale(strengthOut) + scale(strengthIn) + numID + ( scale(strengthOut) + scale(strengthIn) | subID), data=fullData)
# tbl_regression(m) %>% as_gt()
```

## Does directional degree centrality predict memory CLARITY?

\>\>\>

```{r}
m<-lmer( scale(clear) ~  scale(outdegree) + scale(indegree) + numID + ( scale(outdegree) + scale(indegree) | subID), data=fullData)
tbl_regression(m) %>% as_gt()

# StrengthIn/Out analyses from rep pipeline
# m<-lmer( scale(clear) ~  scale(strengthOut) + scale(strengthIn) + numID + ( scale(strengthOut) + scale(strengthIn) | subID), data=fullData)
# tbl_regression(m) %>% as_gt()
```

## Does directional degree centrality predict memory AGENCY?

\>\>\>

```{r}
m<-lmer( scale(agency) ~  scale(outdegree) + scale(indegree) + numID + ( scale(outdegree) + scale(indegree) | subID), data=fullData)
tbl_regression(m) %>% as_gt()

# StrengthIn/Out analyses from rep pipeline
# m<-lmer( scale(agency) ~  scale(strengthOut) + scale(strengthIn) + numID + ( scale(strengthOut) + scale(strengthIn) | subID), data=fullData)
# tbl_regression(m) %>% as_gt()
```

## Does directional degree centrality predict memory EASE OF RECALL?

\>\>\>

```{r}
m<-lmer( scale(easy) ~  scale(outdegree) + scale(indegree) + numID + ( scale(outdegree) + scale(indegree) | subID), data=fullData)
tbl_regression(m) %>% as_gt()

ggpredict(m, terms="outdegree") %>% plot(colors="black") +
  labs(
    x = "Outdegree Centrality",
    y = "Ease of Recall",
    title = "Predicted Effect of Outdegree Centrality on Ease of Recall"
  ) +
  theme(
    axis.title.x = element_text(face = "bold"),
    axis.title.y = element_text(face = "bold")
  )

summary(m)

ease_r2 <- partR2(m)
# StrengthIn/Out analyses from rep pipeline
# m<-lmer( scale(Easy) ~  scale(strengthOut) + scale(strengthIn) + numID + ( scale(strengthOut) + scale(strengthIn) | subID), data=fullData)
# tbl_regression(m) %>% as_gt()
```

## Does directional degree centrality predict memory TRANSFORMATIVENESS?

\>\>\>

```{r}
# Replicating Jake's test - accounting for both outdegree and indegree at the population level
m<-lmer( scale(transformativeness) ~  scale(outdegree) + scale(indegree) + numID + ( scale(outdegree) + scale(indegree) | subID), data=fullData)
tbl_regression(m) %>% as_gt()
summary(m)

ggpredict(m, terms="outdegree") %>% plot(colors="orange") +
  labs(
    x = "Outdegree Centrality",
    y = "Self-Transformativeness",
    title = "Predicted Effect of Outdegree Centrality on Self-Transformativeness"
  ) +
  theme(
    axis.title.x = element_text(face = "bold"),
    axis.title.y = element_text(face = "bold")
  )

transf_r2 <- partR2(m)

# StrengthIn/Out analyses from rep pipeline
# m<-lmer( scale(transformativeness) ~  scale(strengthOut) + scale(strengthIn) + numID + ( scale(strengthOut) + scale(strengthIn) | subID), data=fullData)
# tbl_regression(m) %>% as_gt()
```

## Does directional degree centrality predict memory CHANGEABILITY?

\>\>\>

```{r}
# Replicating Jake's test - accounting for both outdegree and indegree at the population level
m<-lmer( scale(change) ~  scale(outdegree) + scale(indegree) + numID + ( scale(outdegree) + scale(indegree) | subID), data=fullData)
tbl_regression(m) %>% as_gt()



# StrengthIn/Out analyses from rep pipeline
# m<-lmer( scale(change) ~  scale(strengthOut) + scale(strengthIn) + numID + ( scale(strengthOut) + scale(strengthIn) | subID), data=fullData)
# tbl_regression(m) %>% as_gt()
```



##################################################################




# Degree Centrality (Non-directional - overall number of connections)

## Does NON-directional degree centrality predict memory IMPORTANCE?

\>\>\>

```{r}
m <-lmer( scale(importance) ~  scale(degree) + numID + ( scale(degree) | subID), data=fullData)

tbl_regression(m) %>% as_gt()

```

## Does directional degree centrality predict memory CLARITY?

\>\>\>

```{r}
m<-lmer( scale(clear) ~  scale(degree) + numID + ( scale(degree) | subID), data=fullData)
tbl_regression(m) %>% as_gt()

# StrengthIn/Out analyses from rep pipeline
# m<-lmer( scale(clear) ~  scale(strengthOut) + scale(strengthIn) + numID + ( scale(strengthOut) + scale(strengthIn) | subID), data=fullData)
# tbl_regression(m) %>% as_gt()
```

## Does directional degree centrality predict memory AGENCY?

\>\>\>

```{r}
m<-lmer( scale(agency) ~  scale(degree) + numID + ( scale(degree) | subID), data=fullData)
tbl_regression(m) %>% as_gt()

# StrengthIn/Out analyses from rep pipeline
# m<-lmer( scale(agency) ~  scale(strengthOut) + scale(strengthIn) + numID + ( scale(strengthOut) + scale(strengthIn) | subID), data=fullData)
# tbl_regression(m) %>% as_gt()
```

## Does non-directional degree centrality predict memory EASE OF RECALL?

\>\>\>

```{r}
m<-lmer( scale(easy) ~  scale(degree) + numID + ( scale(degree) | subID), data=fullData)
tbl_regression(m) %>% as_gt()

# StrengthIn/Out analyses from rep pipeline
# m<-lmer( scale(Easy) ~  scale(strengthOut) + scale(strengthIn) + numID + ( scale(strengthOut) + scale(strengthIn) | subID), data=fullData)
# tbl_regression(m) %>% as_gt()
```

## Does directional degree centrality predict memory TRANSFORMATIVENESS?

\>\>\>

```{r}
m<-lmer( scale(transformativeness) ~  scale(degree) + numID + ( scale(degree) | subID), data=fullData)
tbl_regression(m) %>% as_gt()

# StrengthIn/Out analyses from rep pipeline
# m<-lmer( scale(transformativeness) ~  scale(strengthOut) + scale(strengthIn) + numID + ( scale(strengthOut) + scale(strengthIn) | subID), data=fullData)
# tbl_regression(m) %>% as_gt()
```

## Does directional degree centrality predict memory CHANGEABILITY?

\>\>\>

```{r}
m<-lmer( scale(change) ~  scale(degree) + numID + ( scale(degree) | subID), data=fullData)
tbl_regression(m) %>% as_gt()

# StrengthIn/Out analyses from rep pipeline
# m<-lmer( scale(change) ~  scale(strengthOut) + scale(strengthIn) + numID + ( scale(strengthOut) + scale(strengthIn) | subID), data=fullData)
# tbl_regression(m) %>% as_gt()
```



# Density (Post-Hoc)

## Descriptives

```{r}
dens <- fullData[, c(1,45)] # For descriptives and later onset file usage
dens <- unique(dens) # Restructure to compare between networks (one dens value per subject)


dens_mean <- mean(dens$dense) # Average network density
dens_sd <- sd(dens$dense) # Standard deviation from density average

dens_freq <- hist(dens$dense) # Distribution of network density across subject networks
dens$density_scaled <- as.vector(scale(dens$dense)) # Scaled density values for lme

write.csv(dens,"densityDf.csv") # Write file to csv for later onset files
```

## Inferences (Linear Mixed Effects Model)

### Does network density predict memory IMPORTANCE?

```{r}
m<-lmer( scale(importance) ~  scale(edgeTot) + numID + ( scale(edgeTot) | subID), data=fullData)
tbl_regression(m) %>% as_gt()
```

### Does network density predict memory CLARITY?

```{r}
m<-lmer( scale(clear) ~  scale(dense) + numID + ( scale(dense) | subID), data=fullData)
tbl_regression(m) %>% as_gt()
```

### Does network density predict memory AGENCY?

```{r}
m<-lmer( scale(agency) ~  scale(dense) + numID + ( scale(dense) | subID), data=fullData)
tbl_regression(m) %>% as_gt()
```

### Does network density predict memory EASE OF RECALL?

```{r}
m<-lmer( scale(easy) ~  scale(dense) + numID + ( scale(dense) | subID), data=fullData)
tbl_regression(m) %>% as_gt()
```

### Does network density predict memory CHANGEABILITY?

```{r}
m<-lmer( scale(change) ~  scale(dense) + numID + ( scale(dense) | subID), data=fullData)
tbl_regression(m) %>% as_gt()
```

### Does network density predict memory TRANSFORMATIVENESS?

```{r}
m<-lmer( scale(transformativeness) ~  scale(dense) + numID + ( scale(dense) | subID), data=fullData)
tbl_regression(m) %>% as_gt()
```


# Edge Total (Post-Hoc)

## Descriptives

# ```{r}
# edgTotal <- fullData[, c(1,45)] # For descriptives and later onset file usage
# edgTotal <- unique(edgTotal) # Restructure to compare between networks (one dens value per subject)
# edgTotal$edg_scaled <- as.vector(scale(edgTotal$edgeTot)) # Scaled density values for lme
# 
# edgTotal_mean <- mean(edgTotal$edgeTot) # Average network density
# edgTotal_sd <- sd(edgTotal$edgeTot) # Standard deviation from density average
# 
# edgTotal_freq <- hist(edgTotal$edgeTot) # Distribution of network density across subject networks
# 
# write.csv(edgTotal,"edgeTotalDf.csv") # Write file to csv for later onset files
# ```

## Inferences (Linear Mixed Effects Model)

### Does network edge total predict memory IMPORTANCE?

```{r}
m<-lmer( scale(change) ~  scale(dense) + numID + ( scale(dense) | subID), data=fullData)
tbl_regression(m) %>% as_gt()
```

### Does network edge total predict memory CLARITY?

```{r}
m<-lmer( scale(clear) ~  scale(dense) + numID + ( scale(dense) | subID), data=fullData)
tbl_regression(m) %>% as_gt()

```

### Does network edge total predict memory AGENCY?

```{r}
m<-lmer( scale(agency) ~  scale(dense) + numID + ( scale(dense) | subID), data=fullData)
tbl_regression(m) %>% as_gt()
```

### Does network edge total predict memory EASE OF RECALL?

```{r}
m<-lmer( scale(easy) ~  scale(dense) + numID + ( scale(dense) | subID), data=fullData)
tbl_regression(m) %>% as_gt()
```

### Does network edge total predict memory CHANGEABILITY?

```{r}
m<-lmer( scale(change) ~  scale(dense) + numID + ( scale(dense) | subID), data=fullData)
tbl_regression(m) %>% as_gt()
```


### Does network edge total predict memory TRANSFORMATIVENESS?

```{r}
m<-lmer( scale(transformativeness) ~  scale(dense) + numID + ( scale(dense) | subID), data=fullData)
tbl_regression(m) %>% as_gt()
```


# Visualizations

## Fundamental (FUND)

```{r}
mF<-lmer( scale(Fund) ~  scale(outdegree) + scale(indegree) + numID + ( scale(outdegree) + scale(indegree) | subID), data=fullData)
tidy(mF)


tbl_regression(mF) %>% as_gt()
ggpredict(m, terms="outdegree") %>% plot(colors="orange") +
  labs(
    x = "Outdegree Centrality",
    y = "Fundamental (Study 2)",
  )
```

## Representative (REP)

```{r}
mR<-lmer( scale(Rep) ~  scale(outdegree) + scale(indegree) + numID + ( scale(outdegree) + scale(indegree) | subID), data=fullData)
tidy(mR)

tbl_regression(mR) %>% as_gt()
ggpredict(m, terms="outdegree") %>% plot(colors="blue") +
  labs(
    x = "Outdegree Centrality",
    y = "Representative (Study 2)",
  )
```

## Changeability (CHAN)

```{r}
mC<-lmer( scale(Chan) ~  scale(outdegree) + scale(indegree) + numID + ( scale(outdegree) + scale(indegree) | subID), data=fullData)
tidy(mC)


tbl_regression(mC) %>% as_gt()
ggpredict(m, terms="outdegree") %>% plot(colors="brown") +
  labs(
    x = "Outdegree Centrality",
    y = "Transformative (Study 2)",
  )
```

## Memory Maps Extension Power Analysis
```{r}

```

