---
title: "MM_SupplementalAnalyses"
author: "Jennifer Mosley"
date: "2024-09-08"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyr)
library(dplyr)
library(lubridate)
library(lmerTest)
library(gtsummary)
library(report)
library(kableExtra)
library(sjPlot)
```

## Supplemental Analyses

```{r}
# Import datasets and merge

# Import individual differences (ID) data set
Df <- read.csv("cleaned_S1.csv")
Df <- Df[-c(1)]
Df <- Df[-c(684)] # Remove check column

subID <- select(Df,c("loginID"))
ID <- Df[ ,639:729]

data <- cbind(subID,ID) # Use this for individual differences/demo analysis

# Import centrality data set
cent <- read.csv("centralityDf_48.csv")
cent <- cent[-c(1)] # Remove extraneous column in front
# Remove sub22 from the centrality dataset, as they are not included in the in-scan ratings data
cent <- cent[cent$subID != "22", ]

# Import density data set
dense <- read.csv("density.csv")
dense <- dense[-c(1)] # Remove extraneous column in front

netmetrics <- cbind(cent,dense)

# Import in-scan memory ratings
inscan <- read.csv("scan_ratings.csv")
inscan <- inscan[-c(1)] # Remove extraneous column in front

fullData <- read.csv("fullData48.csv")
fullData <- fullData[-c(1)] # Remove extraneous column in front
fullData <- fullData[fullData$subID != 22, ]

```

# Individual Differences

## Recode/Reverse scores
```{r}
# Rosenberg Self-Esteem Scale
RSE <- data[2:11]

RSE <- RSE %>%
  mutate(RSE3 = case_when(
    RSE3 == 1 ~ 4,
    RSE3 == 2 ~ 3,
    RSE3 == 4 ~ 1,
    RSE3 == 3 ~ 2,
    TRUE ~ RSE3  # Keep the original value if none of the conditions are met
  ))

RSE <- RSE %>%
  mutate(RSE5 = case_when(
    RSE5 == 1 ~ 4,
    RSE5 == 2 ~ 3,
    RSE5 == 4 ~ 1,
    RSE5 == 3 ~ 2,
    TRUE ~ RSE5  # Keep the original value if none of the conditions are met
  ))

RSE <- RSE %>%
  mutate(RSE8 = case_when(
    RSE8 == 1 ~ 4,
    RSE8 == 2 ~ 3,
    RSE8 == 4 ~ 1,
    RSE8 == 3 ~ 2,
    TRUE ~ RSE8  # Keep the original value if none of the conditions are met
  ))

RSE <- RSE %>%
  mutate(RSE9 = case_when(
    RSE9 == 1 ~ 4,
    RSE9 == 2 ~ 3,
    RSE9 == 4 ~ 1,
    RSE9 == 3 ~ 2,
    TRUE ~ RSE9  # Keep the original value if none of the conditions are met
  ))

RSE <- RSE %>%
  mutate(RSE10 = case_when(
    RSE10 == 1 ~ 4,
    RSE10 == 2 ~ 3,
    RSE10 == 4 ~ 1,
    RSE10 == 3 ~ 2,
    TRUE ~ RSE10  # Keep the original value if none of the conditions are met
  ))

RSE_sum <- rowSums(RSE,na.rm = TRUE)
RSE_sum <- as.vector(RSE_sum)

RSE$RSE_sum <- RSE_sum

sums <- select(data,c("loginID"))
sums$RSE <- RSE_sum # Max possible: 40; higher score, higher self-esteem

# Need for Cognition
NFC <- data[12:17]

# Items 3,4 are reverse scored (reverse agreement for low need for cognition)
NFC <- NFC %>%
  mutate(NFC.6_3 = case_when(
    NFC.6_3 == 1 ~ 4,
    NFC.6_3 == 2 ~ 3,
    NFC.6_3 == 4 ~ 1,
    NFC.6_3 == 3 ~ 2,
    TRUE ~ NFC.6_3  # Keep the original value if none of the conditions are met
  ))

NFC <- NFC %>%
  mutate(NFC.6_4 = case_when(
    NFC.6_4 == 1 ~ 4,
    NFC.6_4 == 2 ~ 3,
    NFC.6_4 == 4 ~ 1,
    NFC.6_4 == 3 ~ 2,
    TRUE ~ NFC.6_4  # Keep the original value if none of the conditions are met
  ))

NFC_sum <- rowSums(NFC,na.rm = TRUE)
NFC_sum <- as.vector(NFC_sum)
sums$NFC <-NFC_sum  # Max possible: 30; higher score, higher need for cognition

# Self-Concept Clarity
SCC <- data[18:29]

# Items 1,2,3,4,5,7,8,9,10,12 are reverse scored (reverse agreement for low self-concept clarity)
SCC <- SCC %>%
  mutate(SCC1 = case_when(
    SCC1 == 1 ~ 5,
    SCC1 == 2 ~ 4,
    SCC1 == 4 ~ 2,
    SCC1 == 5 ~ 1,
    TRUE ~ SCC1  # Keep the original value if none of the conditions are met
  ))

SCC <- SCC %>%
  mutate(SCC2 = case_when(
    SCC2 == 1 ~ 5,
    SCC2 == 2 ~ 4,
    SCC2 == 4 ~ 2,
    SCC2 == 5 ~ 1,
    TRUE ~ SCC2  # Keep the original value if none of the conditions are met
  ))

SCC <- SCC %>%
  mutate(SCC3 = case_when(
    SCC3 == 1 ~ 5,
    SCC3 == 2 ~ 4,
    SCC3 == 4 ~ 2,
    SCC3 == 5 ~ 1,
    TRUE ~ SCC3  # Keep the original value if none of the conditions are met
  ))

SCC <- SCC %>%
  mutate(SCC4 = case_when(
    SCC4 == 1 ~ 5,
    SCC4 == 2 ~ 4,
    SCC4 == 4 ~ 2,
    SCC4 == 5 ~ 1,
    TRUE ~ SCC4  # Keep the original value if none of the conditions are met
  ))

SCC <- SCC %>%
  mutate(SCC5 = case_when(
    SCC5 == 1 ~ 5,
    SCC5 == 2 ~ 4,
    SCC5 == 4 ~ 2,
    SCC5 == 5 ~ 1,
    TRUE ~ SCC5  # Keep the original value if none of the conditions are met
  ))

SCC <- SCC %>%
  mutate(SCC7 = case_when(
    SCC7 == 1 ~ 5,
    SCC7 == 2 ~ 4,
    SCC7 == 4 ~ 2,
    SCC7 == 5 ~ 1,
    TRUE ~ SCC7  # Keep the original value if none of the conditions are met
  ))

SCC <- SCC %>%
  mutate(SCC8 = case_when(
    SCC8 == 1 ~ 5,
    SCC8 == 2 ~ 4,
    SCC8 == 4 ~ 2,
    SCC8 == 5 ~ 1,
    TRUE ~ SCC8  # Keep the original value if none of the conditions are met
  ))

SCC <- SCC %>%
  mutate(SCC9 = case_when(
    SCC9 == 1 ~ 5,
    SCC9 == 2 ~ 4,
    SCC9 == 4 ~ 2,
    SCC9 == 5 ~ 1,
    TRUE ~ SCC9  # Keep the original value if none of the conditions are met
  ))

SCC <- SCC %>%
  mutate(SCC10 = case_when(
    SCC10 == 1 ~ 5,
    SCC10 == 2 ~ 4,
    SCC10 == 4 ~ 2,
    SCC10 == 5 ~ 1,
    TRUE ~ SCC10  # Keep the original value if none of the conditions are met
  ))

SCC <- SCC %>%
  mutate(SCC12 = case_when(
    SCC12 == 1 ~ 5,
    SCC12 == 2 ~ 4,
    SCC12 == 4 ~ 2,
    SCC12 == 5 ~ 1,
    TRUE ~ SCC12  # Keep the original value if none of the conditions are met
  ))

SCC_sum <- rowSums(SCC,na.rm = TRUE)
SCC_sum <- as.vector(SCC_sum)
sums$SCC <- SCC_sum # Max possible: 60; higher score, higher self-concept clarity


# S-DS, Self-Discrepancy Scale
DSS <- data[30:43]

# Items 1,5,6,7,9,14 are reverse scored
DSS <- DSS %>%
  mutate(DS.S_1 = case_when(
    DS.S_1 == 1 ~ 7,
    DS.S_1 == 2 ~ 6,
    DS.S_1 == 7 ~ 1,
    DS.S_1 == 6 ~ 2,
    TRUE ~ DS.S_1  # Keep the original value if none of the conditions are met
  ))

DSS <- DSS %>%
  mutate(DS.S_5 = case_when(
    DS.S_5 == 1 ~ 7,
    DS.S_5 == 2 ~ 6,
    DS.S_5 == 7 ~ 1,
    DS.S_5 == 6 ~ 2,
    TRUE ~ DS.S_5  # Keep the original value if none of the conditions are met
  ))

DSS <- DSS %>%
  mutate(DS.S_6 = case_when(
    DS.S_6 == 1 ~ 7,
    DS.S_6 == 2 ~ 6,
    DS.S_6 == 7 ~ 1,
    DS.S_6 == 6 ~ 2,
    TRUE ~ DS.S_6  # Keep the original value if none of the conditions are met
  ))

DSS <- DSS %>%
  mutate(DS.S_7 = case_when(
    DS.S_7 == 1 ~ 7,
    DS.S_7 == 2 ~ 6,
    DS.S_7 == 7 ~ 1,
    DS.S_7 == 6 ~ 2,
    TRUE ~ DS.S_7  # Keep the original value if none of the conditions are met
  ))

DSS <- DSS %>%
  mutate(DS.S_9 = case_when(
    DS.S_9 == 1 ~ 7,
    DS.S_9 == 2 ~ 6,
    DS.S_9 == 7 ~ 1,
    DS.S_9 == 6 ~ 2,
    TRUE ~ DS.S_9  # Keep the original value if none of the conditions are met
  ))

DSS <- DSS %>%
  mutate(DS.S_14 = case_when(
    DS.S_14 == 1 ~ 7,
    DS.S_14 == 2 ~ 6,
    DS.S_14 == 7 ~ 1,
    DS.S_14 == 6 ~ 2,
    TRUE ~ DS.S_14  # Keep the original value if none of the conditions are met
  ))

DSS_sum <- rowSums(DSS,na.rm = TRUE)
DSS_sum <- as.vector(DSS_sum)
sums$DSS <- DSS_sum # Max possible: 98; Higher score, higher self-discrepancy (lower self-concept clarity)

# Center for Epidemiologic Studies Depression Scale (CESD)
CESD <- data[44:63]

# Items 4,8,12,16 are reverse scored
CESD <- CESD %>%
  mutate(CESD4 = case_when(
    CESD4 == 1 ~ 4,
    CESD4 == 2 ~ 3,
    CESD4 == 4 ~ 1,
    CESD4 == 3 ~ 2,
    TRUE ~ CESD4  # Keep the original value if none of the conditions are met
  ))

CESD <- CESD %>%
  mutate(CESD8 = case_when(
    CESD8 == 1 ~ 4,
    CESD8 == 2 ~ 3,
    CESD8 == 4 ~ 1,
    CESD8 == 3 ~ 2,
    TRUE ~ CESD8  # Keep the original value if none of the conditions are met
  ))

CESD <- CESD %>%
  mutate(CESD12 = case_when(
    CESD12 == 1 ~ 4,
    CESD12 == 2 ~ 3,
    CESD12 == 4 ~ 1,
    CESD12 == 3 ~ 2,
    TRUE ~ CESD12  # Keep the original value if none of the conditions are met
  ))

CESD <- CESD %>%
  mutate(CESD16 = case_when(
    CESD16 == 1 ~ 4,
    CESD16 == 2 ~ 3,
    CESD16 == 4 ~ 1,
    CESD16 == 3 ~ 2,
    TRUE ~ CESD16  # Keep the original value if none of the conditions are met
  ))

CESD_sum <- rowSums(CESD,na.rm = TRUE)
CESD_sum <- as.vector(CESD_sum)
sums$CESD <- CESD_sum # Max possible: 60; Higher score, higher depressive symptomatology

# Subjective Happiness Scale (SHS)
SHS <- data[64:67]

# Items 4 is reversed scored
SHS <- SHS %>%
  mutate(SHS4 = case_when(
    SHS4 == 7 ~ 1,
    SHS4 == 6 ~ 2,
    SHS4 == 1 ~ 7,
    SHS4 == 2 ~ 6,
    TRUE ~ SHS4  # Keep the original value if none of the conditions are met
  ))

SHS_sum <- rowSums(SHS,na.rm = TRUE)
SHS_sum <- as.vector(SHS_sum)
sums$SHS <- SHS_sum # Max possible: 28; Higher score, higher subjective happiness

# Rumination-Reflection Questionnaire (RRQ)
RRQ <- data[68:91]

# Items 6,9,10,13,14,17,20,24 is reversed scored
RRQ <- RRQ %>%
  mutate(RRQ_6 = case_when(
    RRQ_6 == 5 ~ 1,
    RRQ_6 == 2 ~ 2,
    RRQ_6 == 1 ~ 5,
    RRQ_6 == 2 ~ 4,
    TRUE ~ RRQ_6  # Keep the original value if none of the conditions are met
  ))

RRQ <- RRQ %>%
  mutate(RRQ_9 = case_when(
    RRQ_9 == 5 ~ 1,
    RRQ_9 == 2 ~ 2,
    RRQ_9 == 1 ~ 5,
    RRQ_9 == 2 ~ 4,
    TRUE ~ RRQ_9  # Keep the original value if none of the conditions are met
  ))

RRQ <- RRQ %>%
  mutate(RRQ_10 = case_when(
    RRQ_10 == 5 ~ 1,
    RRQ_10 == 2 ~ 2,
    RRQ_10 == 1 ~ 5,
    RRQ_10 == 2 ~ 4,
    TRUE ~ RRQ_10  # Keep the original value if none of the conditions are met
  ))

RRQ <- RRQ %>%
  mutate(RRQ_13 = case_when(
    RRQ_13 == 5 ~ 1,
    RRQ_13 == 2 ~ 2,
    RRQ_13 == 1 ~ 5,
    RRQ_13 == 2 ~ 4,
    TRUE ~ RRQ_13  # Keep the original value if none of the conditions are met
  ))

RRQ <- RRQ %>%
  mutate(RRQ_14 = case_when(
    RRQ_14 == 5 ~ 1,
    RRQ_14 == 2 ~ 2,
    RRQ_14 == 1 ~ 5,
    RRQ_14 == 2 ~ 4,
    TRUE ~ RRQ_14  # Keep the original value if none of the conditions are met
  ))

RRQ <- RRQ %>%
  mutate(RRQ_17 = case_when(
    RRQ_17 == 5 ~ 1,
    RRQ_17 == 2 ~ 2,
    RRQ_17 == 1 ~ 5,
    RRQ_17 == 2 ~ 4,
    TRUE ~ RRQ_17  # Keep the original value if none of the conditions are met
  ))

RRQ <- RRQ %>%
  mutate(RRQ_20 = case_when(
    RRQ_20 == 5 ~ 1,
    RRQ_20 == 2 ~ 2,
    RRQ_20 == 1 ~ 5,
    RRQ_20 == 2 ~ 4,
    TRUE ~ RRQ_20  # Keep the original value if none of the conditions are met
  ))

RRQ <- RRQ %>%
  mutate(RRQ_24 = case_when(
    RRQ_24 == 5 ~ 1,
    RRQ_24 == 2 ~ 2,
    RRQ_24 == 1 ~ 5,
    RRQ_24 == 2 ~ 4,
    TRUE ~ RRQ_24  # Keep the original value if none of the conditions are met
  ))


RRQ_Rum <- select(RRQ,c("RRQ_1","RRQ_2","RRQ_3","RRQ_4","RRQ_5","RRQ_6","RRQ_7",
                        "RRQ_8","RRQ_9","RRQ_10","RRQ_11","RRQ_12"))
RRQ_Rum$Rum_mean <- rowMeans(RRQ_Rum, na.rm = TRUE)

RRQ_Ref <- select(RRQ,c("RRQ_13","RRQ_14","RRQ_15","RRQ_16","RRQ_17","RRQ_18","RRQ_19",
                        "RRQ_20","RRQ_21","RRQ_22","RRQ_23","RRQ_24"))
RRQ_Ref$Ref_mean <- rowMeans(RRQ_Ref, na.rm = TRUE)

RRQ <- RRQ %>%
  mutate(Ref_mean = RRQ_Ref$Ref_mean)

RRQ <- RRQ %>%
  mutate(Rum_mean = RRQ_Rum$Rum_mean)

RRQ_stats <- select(RRQ,c("Ref_mean", "Rum_mean"))

sums <- bind_cols(sums, RRQ_stats) # Rumination vs. Reflection
```

## Repeat individual differences for centrality/ratings dataframe
```{r}
repeat_data_df <- function(df, n_times) {
  # Use the `rep()` function to repeat the indices of the dataframe
  repeated_df <- df[rep(1:nrow(df), each = n_times), ]
  
  # Return the repeated dataframe
  return(repeated_df)
}

individual_data <- repeat_data_df(sums, 24)
individual_data <- individual_data[individual_data$loginID != "22", ]
```

## Combine all datasets and finalize
```{r}
# Be sure to run the rest of the script before this, depends on dimensions after processing.


# Force combine datasets that are off by a single observation
full_index <- seq_len(max(nrow(individual_data), nrow(netmetrics)))

# Align df1
df1_aligned <- individual_data[full_index, , drop = FALSE]
df1_aligned[is.na(df1_aligned)] <- NA

# Align df2
df2_aligned <- netmetrics[full_index, , drop = FALSE]
df2_aligned[is.na(df2_aligned)] <- NA

# Combine aligned dataframes
data2 <- cbind(df1_aligned, df2_aligned)

data <- cbind(data2,inscan)

# Remove extra subID columns 
data <- select(data, -subID)

# Set numeric columns to numeric
data$valRate <- as.numeric(data$valRate)
data$intenseRate <- as.numeric(data$intenseRate)
data$vividRate <- as.numeric(data$vividRate)

# Remove 22 from sums
sums <- sums[data$loginID != 22, ]

ratings <- fullData[, c(24:29,33)] # Remove extraneous column in front

# Repeat first row of data to pad for later cbind
first_row <- ratings[1, ]
ratings <- rbind(first_row, ratings)
ratings[1, ] <- NA

all <- cbind(data,ratings)

# centUnique <- cent[! duplicated(cent$subID), ]
# sums_cent <- cbind(sums,centUnique) 
# sums_cent <- sums_cent[,-c(10)] # Remove extra subject ID col
# 
# denseUnique <- dense[! duplicated(dense$subID), ]
# sums_dense <- cbind(sums,denseUnique)
# sums_dense <- sums_dense[,-c(10)] # Remove extra subject ID col
```


```{r}
# Set numID
numID = 24
```

# Analyses (lmer)

# Predicting memory RATINGS from outdegree x individual differences
```{r}
m1 <- lmer(scale(transformativeness) ~ scale(RSE) + scale(outdegree) + (scale(RSE) * scale(outdegree)) + (scale(outdegree) | loginID), data=all)
tab_model(m1)

#tbl_regression(m1) %>% as_gt()
#summary(m1)
```

```{r}
m2 <- lmer(scale(valRate) ~ scale(Rum_mean) + scale(outdegree) + (scale(Rum_mean) * scale(outdegree)) + (scale(outdegree) | loginID), data=all)
tab_model(m2)

#tbl_regression(m1) %>% as_gt()
#summary(m1)
```

```{r}
m3 <- lmer(scale(importance) ~ scale(SCC) + scale(outdegree) + (scale(SCC) * scale(outdegree)) + (scale(outdegree) | loginID), data=all)
tab_model(m3)

#tbl_regression(m1) %>% as_gt()
#summary(m1)
```

```{r}
m4 <- lmer(scale(clear) ~ scale(Ref_mean) + scale(outdegree) + (scale(Ref_mean) * scale(outdegree)) + (scale(outdegree) | loginID), data=all)
tab_model(m4)

#tbl_regression(m1) %>% as_gt()
#summary(m1)
```

```{r}
m5 <- lmer(scale(easy) ~ scale(Ref_mean) + scale(outdegree) + (scale(Ref_mean) * scale(outdegree)) + (scale(outdegree) | loginID), data=all)
tab_model(m5)

#tbl_regression(m1) %>% as_gt()
#summary(m1)
```

```{r}
m6 <- lmer(scale(agency) ~ scale(SHS) + scale(outdegree) + (scale(SHS) * scale(outdegree)) + (scale(outdegree) | loginID), data=all)
tab_model(m6)

#tbl_regression(m1) %>% as_gt()
#summary(m1)
```

```{r}
m7 <- lmer(scale(change) ~ scale(Rum_mean) + scale(outdegree) + (scale(Rum_mean) * scale(outdegree)) + (scale(outdegree) | loginID), data=all)
tab_model(m7)

#tbl_regression(m1) %>% as_gt()
#summary(m1)
```

```{r}
m8 <- lmer(scale(recency_sum) ~ scale(Rum_mean) + scale(outdegree) + (scale(Rum_mean) * scale(outdegree)) + (scale(outdegree) | loginID), data=all)
tab_model(m8)

#tbl_regression(m1) %>% as_gt()
#summary(m1)
```



# Predicting memory RATINGS from indegree x individual differences
```{r}
m1 <- lmer(scale(transformativeness) ~ scale(Ref_mean) + scale(indegree) + (scale(Ref_mean) * scale(indegree)) + (scale(indegree) | loginID), data=all)
tab_model(m1)

#tbl_regression(m1) %>% as_gt()
#summary(m1)
```

```{r}
m2 <- lmer(scale(valRate) ~ scale(RSE) + scale(indegree) + (scale(RSE) * scale(indegree)) + (scale(indegree) | loginID), data=all)
tab_model(m2)

#tbl_regression(m1) %>% as_gt()
#summary(m1)
```

```{r}
m3 <- lmer(scale(importance) ~ scale(Rum_mean) + scale(indegree) + (scale(Rum_mean) * scale(indegree)) + (scale(indegree) | loginID), data=all)
tab_model(m3)

#tbl_regression(m1) %>% as_gt()
#summary(m1)
```

```{r}
m4 <- lmer(scale(clear) ~ scale(Rum_mean) + scale(indegree) + (scale(Rum_mean) * scale(indegree)) + (scale(indegree) | loginID), data=all)
tab_model(m4)

#tbl_regression(m1) %>% as_gt()
#summary(m1)
```

```{r}
m5 <- lmer(scale(easy) ~ scale(Rum_mean) + scale(indegree) + (scale(Rum_mean) * scale(indegree)) + (scale(indegree) | loginID), data=all)
tab_model(m5)

#tbl_regression(m1) %>% as_gt()
#summary(m1)
```

```{r}
m6 <- lmer(scale(agency) ~ scale(Rum_mean) + scale(indegree) + (scale(Rum_mean) * scale(indegree)) + (scale(indegree) | loginID), data=all)
tab_model(m6)

#tbl_regression(m1) %>% as_gt()
#summary(m1)
```

```{r}
m7 <- lmer(scale(change) ~ scale(Rum_mean) + scale(indegree) + (scale(Rum_mean) * scale(indegree)) + (scale(indegree) | loginID), data=all)
tab_model(m7)

#tbl_regression(m1) %>% as_gt()
#summary(m1)
```

```{r}
m8 <- lmer(scale(recency_sum) ~ scale(Rum_mean) + scale(indegree) + (scale(Rum_mean) * scale(indegree)) + (scale(indegree) | loginID), data=all)
tab_model(m8)

#tbl_regression(m1) %>% as_gt()
#summary(m1)
```



## Predicting recall ratings from network centrality
```{r}
# Predicting memory recall valence from centrality (directional)
valence_cent <-lmer( scale(valRate) ~  scale(outdegree) + scale(indegree) + ( scale(outdegree) + scale(indegree) | loginID), data=data)
tbl_regression(valence_cent) %>% as_gt()

#report(m1)
```

```{r}
# Predicting memory recall affective intensity from centrality (directional)
intense_cent <-lmer( scale(intenseRate) ~  scale(outdegree) + scale(indegree) + ( scale(outdegree) + scale(indegree) | loginID), data=data)
tbl_regression(intense_cent) %>% as_gt()
```

```{r}
# Predicting memory recall vividness from centrality (directional)
vivid_cent <-lmer( scale(vividRate) ~  scale(outdegree) + scale(indegree) + ( scale(outdegree) + scale(indegree) | loginID), data=data)
tbl_regression(vivid_cent) %>% as_gt()
```


```{r}
# Predicting memory recall valence from centrality (non-directional)
valence_overall <-lmer( scale(valRate) ~  scale(degree) + ( scale(degree) | loginID), data=data)
tbl_regression(valence_overall) %>% as_gt()
```

```{r}
# Predicting memory recall affective intensity from centrality (non-directional)
intense_overall <-lmer( scale(intenseRate) ~  scale(degree) + ( scale(degree) | loginID), data=data)
tbl_regression(intense_overall) %>% as_gt()
```

```{r}
# Predicting memory recall vividness from centrality (non-directional)
vivid_overall <-lmer( scale(vividRate) ~  scale(degree) + ( scale(degree) | loginID), data=data)
tbl_regression(vivid_overall) %>% as_gt()
```

##  Predicting individual differences from network centrality
```{r}
# Does centrality predict RSE?
RSE_cent <-lmer( scale(RSE)  ~  scale(outdegree) + scale(indegree) + ( scale(outdegree) + scale(indegree) | loginID), data=data)
tbl_regression(RSE_cent) %>% as_gt()
```

```{r}
# Does centrality predict NFC?
NFC_cent <-lmer( scale(NFC)  ~  scale(outdegree) + scale(indegree) + ( scale(outdegree) + scale(indegree) | loginID), data=data)
tbl_regression(NFC_cent) %>% as_gt()
```

```{r}
# Does centrality predict SCC?
SCC_cent <-lmer( scale(SCC)  ~  scale(outdegree) + scale(indegree) + ( scale(outdegree) + scale(indegree) | loginID), data=data)
tbl_regression(SCC_cent) %>% as_gt()
```

```{r}
# Does centrality predict SD-S?
SDS_cent <-lmer( scale(DSS)  ~  scale(outdegree) + scale(indegree) + ( scale(outdegree) + scale(indegree) | loginID), data=data)
tbl_regression(SDS_cent) %>% as_gt()
```

```{r}
# Does centrality predict CESD?
CESD_cent <-lmer( scale(CESD)  ~  scale(outdegree) + scale(indegree) + ( scale(outdegree) + scale(indegree) | loginID), data=data)
tbl_regression(CESD_cent) %>% as_gt()

# VERY odd confidence intervals, should probably re-run if interested in interpreting
```

```{r}
# Does centrality predict SHS?
SHS_cent <-lmer( scale(SHS)  ~  scale(outdegree) + scale(indegree)+( scale(outdegree) + scale(indegree) | loginID), data=data)
tbl_regression(SHS_cent) %>% as_gt()
```


```{r}
# Does centrality predict Reflection?
Ref_cent <-lmer( scale(Ref_mean)  ~  scale(outdegree) + scale(indegree) + ( scale(outdegree) + scale(indegree) | loginID), data=data)
tbl_regression(Ref_cent) %>% as_gt()
```

```{r}
# Does centrality predict Rumination?
Rum_cent <-lmer( scale(Rum_mean)  ~  scale(outdegree) + scale(indegree) + ( scale(outdegree) + scale(indegree) | loginID), data=data)
tbl_regression(Rum_cent) %>% as_gt()
```


##############################################################################
##############################################################################
##############################################################################


##  Predicting individual differences from network density

```{r}
# Remove subj2 - lack of density values? N = 46 (excluding 22 and 2 from centrality analyses)
data <- data[data$loginID != 2, ]

# dens <- read_csv("densityDf.csv")
# dens <- dens[ ,-c(1,2)]

# dense <- dense[-c(1:23), , drop = FALSE]

denseModel <- cbind(iDiffs,dens)
#denseModel<- denseModel[!duplicated(denseModel$loginID), ]
```
```{r}
# Define the function to calculate and combine correlation results
calculate_correlations <- function(data, var_pairs) {
  results <- list()  # Initialize an empty list to store correlation results
  
  # Loop over each pair of variables
  for (i in 1:nrow(var_pairs)) {
    var1 <- var_pairs[i, 1]
    var2 <- var_pairs[i, 2]
    
    # Calculate correlation
    cor_test <- cor.test(as.matrix(data[, c(var1, var2)]))
    cor_value <- cor_test$r[1, 2]    # Extract the correlation value
    p_value <- cor_test$P[1, 2]      # Extract the p-value
    
    # Store results in a list
    results[[i]] <- data.frame(
      Variable1 = var1,
      Variable2 = var2,
      Correlation = round(cor_value, 3),
      P_value = round(p_value, 3)
    )
  }
  
  # Combine results into a single dataframe
  results_df <- bind_rows(results)
  
  return(results_df)
}
```


```{r}
# Does centrality predict RSE?
#RSE_dens <-lmer( scale(RSE) ~ scale(dense) + ( scale(dense) | loginID), data=data)

#m10 <-lm( scale(transformativeness) ~ scale(RSE) + scale(dense) + (scale(CESD) + scale(dense)), data=all)

m10 <- cor.test(scale(all$dense),scale(all$RSE),method = "pearson") ##
tab_model(m10)

m11 <- cor.test(scale(all$dense),scale(all$NFC),method = "pearson")
tab_model(m11)

m12 <- cor.test(scale(all$dense),scale(all$SCC),method = "pearson")
tab_model(m12)

m13 <- cor.test(scale(all$dense),scale(all$DSS),method = "pearson") ##
tab_model(m13)

m14 <- cor.test(scale(all$dense),scale(all$CESD),method = "pearson") ##
tab_model(m14)

m15 <- cor.test(scale(all$dense),scale(all$SHS),method = "pearson") ##
tab_model(m15)

m16 <- cor.test(scale(all$dense),scale(all$Ref_mean),method = "pearson")
tab_model(m16)

m17 <- cor.test(scale(all$dense),scale(all$Rum_mean),method = "pearson") ##
tab_model(m17)

#report(m10)
#tab_model(m10)
```

```{r}
# Does centrality predict NFC?
NFC_dens <-lmer( scale(NFC)  ~  scale(dense) + ( scale(dense) | loginID), data=data)
tbl_regression(NFC_dens) %>% as_gt()
```

```{r}
# Does centrality predict SCC?
SCC_dense <-lmer(scale(SCC)  ~  scale(dense) + ( scale(dense) | loginID), data=data) 
tbl_regression(SCC_dense) %>% as_gt()
```

```{r}
# Does centrality predict SD-S?
SDS_cent <-lmer( scale(DSS)  ~  scale(dense) + (scale(dense) | loginID), data=data)
tbl_regression(SDS_cent) %>% as_gt()
```


```{r}
# Does centrality predict CESD?
CESD_dense <-lmer( scale(CESD)  ~  scale(dense) + (scale(dense) | loginID), data=data)
tbl_regression(CESD_dense) %>% as_gt()

# VERY odd confidence intervals, should probably re-run if interested in interpreting
```

```{r}
# Does centrality predict SHS?
SHS_dense <-lmer( scale(SHS)  ~  scale(dense) + ( scale(dense) | loginID), data=data)
tbl_regression(SHS_dense) %>% as_gt()
```


```{r}
# Does centrality predict Reflection?
Ref_dense <-lmer( scale(Ref_mean)  ~  scale(dense)+ ( scale(dense) | loginID), data=data)
tbl_regression(Ref_dense) %>% as_gt()
```

```{r}
# Does centrality predict Rumination?
Rum_dense <-lmer( scale(Rum_mean)  ~  scale(dense) + ( scale(dense) | loginID), data=data)
tbl_regression(Rum_cent) %>% as_gt()
```

